---
title: "Psychology Training Clinics: 2026 APTC Comprehensive Analysis"
author: "Jacqueline Hersh, Ph.D. & Ryan L. Farmer, Ph.D."
date: today
format:
  html:
    toc: true
    toc-depth: 3
    toc-float: true
    number-sections: true
    code-fold: true
    code-tools: true
    theme: cosmo
    df-print: paged
    fig-width: 10
    fig-height: 6
editor: visual
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  message = FALSE,
  fig.align = 'center'
)

# APTC Color Palette
aptc_navy <- "#252b3b"
aptc_coral <- "#ff6544"
aptc_teal <- "#31a8c0"
aptc_white <- "#ffffff"

# Color palette for categorical data (using APTC colors + variations)
aptc_palette <- c(aptc_coral, aptc_teal, aptc_navy, "#ff8f77", "#5bc0d4", "#454d5f")

# Binary color scheme (Yes/No, etc.)
aptc_binary <- c(aptc_teal, aptc_coral)

# Sequential color scheme (for gradients)
aptc_sequential <- colorRampPalette(c(aptc_white, aptc_teal, aptc_navy))(100)
```

# Setup and Data Loading

## Load Libraries

```{r libraries}
library(readxl)
library(tidyverse)
library(freqtables)
library(skimr)
library(scales)
library(gt)
library(knitr)
library(kableExtra)
library(patchwork)
library(viridis)
```

## Load Data

```{r load-data}
# Load the data
dat <- read_excel("dat.xlsx")

# Basic data cleaning
dat <- dat %>%
  # Keep only finished responses
  filter(Finished == "True" | Progress == "100") %>%
  # Convert numeric columns (being careful with column names)
  mutate(
    Progress = as.numeric(Progress),
    Duration = as.numeric(`Duration (in seconds)`),
    GrossSalary = as.numeric(GrossSalary),
    FTESalary = as.numeric(FTESalary),
    RoleDuration = as.numeric(RoleDuration),
    ClinicDuration = as.numeric(ClinicDuration),
    ClinicAge = as.numeric(ClinicAge),
    HoursWorkClinic = as.numeric(HoursWorkClinic),
    CoursesTaught = as.numeric(CoursesTaught),
    CourseCreditHours = as.numeric(CourseCreditHours),
    ClinicTotalTrainees = as.numeric(ClinicTotalTrainees),
    ClinicClientsCount = as.numeric(ClinicClientsCount),
    NumRooms = as.numeric(NumRooms),
    ClinSqFt = as.numeric(ClinSqFt),
    SupTraineeCount = as.numeric(SupTraineeCount),
    MaxTraineeCount = as.numeric(MaxTraineeCount),
    HoursSupTherapy = as.numeric(HoursSupTherapy),
    HoursSupAssmnt = as.numeric(HoursSupAssmnt),
    HoursSupSup = as.numeric(HoursSupSup),
    HoursWatching = as.numeric(HoursWatching),
    HoursReviewingDoc = as.numeric(HoursReviewingDoc),
    MaxTraineesTherapy = as.numeric(MaxTraineesTherapy),
    MaxTraineesAssmnt = as.numeric(MaxTraineesAssmnt),
    TxLength = as.numeric(TxLength),
    MaxTxCasesAllow = as.numeric(MaxTxCasesAllow),
    MaxAxCasesAllow = as.numeric(MaxAxCasesAllow),
    ClinicRevenue = as.numeric(ClinicRevenue),
    ClinicTxRevenue = as.numeric(ClinicTxRevenue),
    ClinicAxRevenue = as.numeric(ClinicAxRevenue),
    ClinicTherapyFees_1 = as.numeric(ClinicTherapyFees_1),
    ClinicTherapyFees_2 = as.numeric(ClinicTherapyFees_2),
    ClinicTherapyFees_3 = as.numeric(ClinicTherapyFees_3),
    ClinicAssmntFees_1 = as.numeric(ClinicAssmntFees_1),
    ClinicAssmntFees_2 = as.numeric(ClinicAssmntFees_2),
    ClinicAssmntFees_3 = as.numeric(ClinicAssmntFees_3),
    Burnout_1 = as.numeric(Burnout_1),
    Burnout_2 = as.numeric(Burnout_2),
    Burnout_3 = as.numeric(Burnout_3),
    Burnout_4 = as.numeric(Burnout_4),
    Burnout_5 = as.numeric(Burnout_5),
    TXClientsCount = as.numeric(TXClientsCount),
    TxTraineesCount = as.numeric(TxTraineesCount),
    TxSupCount = as.numeric(TxSupCount),
    AxClientsCount = as.numeric(AxClientsCount),
    AxTraineesCount = as.numeric(AxTraineesCount),
    AxSupCount = as.numeric(AxSupCount),
    Prog1StudentCount = as.numeric(Prog1StudentCount),
    Prog2StudentCount = as.numeric(Prog2StudentCount),
    Prog3StudentCount = as.numeric(Prog3StudentCount),
    FTESupportStaff = as.numeric(FTESupportStaff),
    ClinicSupportStaff = as.numeric(ClinicSupportStaff),
    FTEGradStaff = as.numeric(FTEGradStaff),
    GradStaff = as.numeric(GradStaff),
    UgradStaff = as.numeric(UgradStaff),
    HoursUgradStaff = as.numeric(HoursUgradStaff),
    PostdocCount = as.numeric(PostdocCount),
    ClinicHours = as.numeric(ClinicHours)
  )

# Display sample info
cat("Total respondents:", nrow(dat), "\n")
cat("Number of variables:", ncol(dat), "\n")
```

## Helper Functions

```{r helpers}
# Function to handle NA as empty string
nz <- function(x) ifelse(is.na(x), "", x)

# Functions to identify tenure-track status
is_ntt <- function(x) {
  s <- nz(x)
  str_detect(s, regex("\\bnon[- ]?tenure\\b", ignore_case = TRUE)) |
    str_detect(s, regex("\\b(adjunct|lecturer|teaching|clinical)\\b", ignore_case = TRUE))
}

is_tt <- function(x) {
  s <- nz(x)
  str_detect(s, regex("\\b(tenured|tenure[- ]?track)\\b", ignore_case = TRUE)) &
    !is_ntt(x)
}

# Prepare salary data
dat_simple <- dat %>%
  mutate(
    # Parse salary
    GrossSalary = parse_number(as.character(GrossSalary)),
    GrossSalary = ifelse(is.na(GrossSalary) | GrossSalary <= 0, NA_real_, GrossSalary),
    
    # FT/PT
    FullPart = case_when(
      str_detect(nz(FullPart), regex("part", ignore_case = TRUE)) ~ "Part-time",
      str_detect(nz(FullPart), regex("full", ignore_case = TRUE)) ~ "Full-time",
      TRUE ~ NA_character_
    ),
    
    # Rank groups
    RankGrp = case_when(
      str_detect(nz(Rank), regex("^Assistant", ignore_case = TRUE)) ~ "Assistant Professor",
      str_detect(nz(Rank), regex("^Associate", ignore_case = TRUE)) ~ "Associate Professor",
      str_detect(nz(Rank), regex("^Full", ignore_case = TRUE)) ~ "Full Professor",
      str_detect(nz(RoleTitle), regex("lecturer", ignore_case = TRUE)) |
      str_detect(nz(PositionType), regex("lecturer", ignore_case = TRUE)) ~ "Lecturer",
      str_detect(nz(RoleTitle), regex("staff", ignore_case = TRUE)) ~ "Staff (N/A)",
      !is.na(Rank) ~ "Other (specified)",
      TRUE ~ "Unspecified Rank"
    ),
    RankGrp = factor(
      RankGrp,
      levels = c("Assistant Professor", "Associate Professor", "Full Professor",
                 "Lecturer", "Staff (N/A)", "Other (specified)", "Unspecified Rank")
    )
  )
```

## Data Quality Checks

```{r data-quality-checks}
# Sample size verification
sample_summary <- data.frame(
  Metric = c("Total Responses", "Finished Responses", "Progress = 100%", 
             "Final Analytic Sample"),
  Count = c(
    nrow(read_excel("dat.xlsx")),
    sum(dat$Finished == "True", na.rm = TRUE),
    sum(dat$Progress == 100, na.rm = TRUE),
    nrow(dat)
  )
)

sample_summary %>%
  kable(caption = "Sample Size Verification") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

# Check key categorical variables
cat("\n=== Membership Status ===\n")
print(table(dat$MemStatus, useNA = "always"))

cat("\n=== Professional Degree ===\n")
print(table(dat$ProfDeg, useNA = "always"))

cat("\n=== Teaching Binary ===\n")
print(table(dat$TeachingBinary, useNA = "always"))

cat("\n=== EMR Binary ===\n")
print(table(dat$EMRbinary, useNA = "always"))

cat("\n=== Position Type (first 5 unique values) ===\n")
print(head(sort(table(dat$PositionType, useNA = "always"), decreasing = TRUE), 5))
```

### Missing Data Analysis

```{r missing-data-analysis}
# Calculate missing data for key variables
key_vars <- c(
  "GrossSalary", "FTESalary", "RoleDuration", "ClinicDuration",
  "Rank", "PositionType", "FullPart", "ContractLength",
  "TeachingBinary", "CoursesTaught",
  "ClinicAge", "ClinicTrainingModel", "ClinicTotalTrainees", "ClinicClientsCount",
  "ClinicRevenue", "ClinicSlidingScale",
  "EMRbinary", "Telehealth", "ResearchActive",
  "Burnout_1", "MaxTraineeCount"
)

missing_summary <- dat %>%
  select(any_of(key_vars)) %>%
  summarise(across(everything(), ~sum(is.na(.)))) %>%
  pivot_longer(everything(), names_to = "Variable", values_to = "Missing_Count") %>%
  mutate(
    Total = nrow(dat),
    Percent_Missing = round(100 * Missing_Count / Total, 1),
    Percent_Complete = 100 - Percent_Missing
  ) %>%
  arrange(desc(Percent_Missing))

missing_summary %>%
  filter(Missing_Count > 0) %>%
  kable(caption = "Missing Data Summary (Variables with Any Missing Data)") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

# Flag high missing rates
high_missing <- missing_summary %>%
  filter(Percent_Missing > 20)

if (nrow(high_missing) > 0) {
  cat("\n⚠️ WARNING: The following variables have >20% missing data:\n")
  print(high_missing %>% select(Variable, Percent_Missing))
}
```

### Numeric Data Range Checks

```{r numeric-range-checks}
# Salary checks
salary_checks <- dat %>%
  filter(!is.na(GrossSalary)) %>%
  summarise(
    N = n(),
    Min = min(GrossSalary),
    Q1 = quantile(GrossSalary, 0.25),
    Median = median(GrossSalary),
    Mean = mean(GrossSalary),
    Q3 = quantile(GrossSalary, 0.75),
    Max = max(GrossSalary),
    N_Below_30K = sum(GrossSalary < 30000),
    N_Above_200K = sum(GrossSalary > 200000)
  )

salary_checks %>%
  mutate(across(c(Min, Q1, Median, Mean, Q3, Max), ~dollar(.))) %>%
  kable(caption = "Salary Data Quality Check") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

if (salary_checks$N_Below_30K > 0) {
  cat("\n⚠️ NOTE:", salary_checks$N_Below_30K, "salaries are below $30,000. Please verify these are accurate.\n")
}
if (salary_checks$N_Above_200K > 0) {
  cat("\n⚠️ NOTE:", salary_checks$N_Above_200K, "salaries are above $200,000. Please verify these are accurate.\n")
}

# Revenue checks
revenue_checks <- dat %>%
  filter(!is.na(ClinicRevenue), ClinicRevenue > 0) %>%
  summarise(
    N = n(),
    Min = min(ClinicRevenue),
    Q1 = quantile(ClinicRevenue, 0.25),
    Median = median(ClinicRevenue),
    Mean = mean(ClinicRevenue),
    Q3 = quantile(ClinicRevenue, 0.75),
    Max = max(ClinicRevenue),
    N_Above_500K = sum(ClinicRevenue > 500000),
    N_Above_1M = sum(ClinicRevenue > 1000000)
  )

revenue_checks %>%
  mutate(across(c(Min, Q1, Median, Mean, Q3, Max), ~dollar(.))) %>%
  kable(caption = "Revenue Data Quality Check") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

if (revenue_checks$N_Above_1M > 0) {
  cat("\n⚠️ NOTE:", revenue_checks$N_Above_1M, "clinics report revenue above $1,000,000.\n")
  cat("These are excluded from some visualizations. Consider if these are accurate or should be included.\n")
}
```

### Tenure Track Classification Verification

```{r tenure-classification-check}
# Check tenure track classification
tenure_check <- dat %>%
  filter(!is.na(PositionType)) %>%
  mutate(
    TT = is_tt(PositionType),
    NTT = is_ntt(PositionType),
    Classification = case_when(
      TT & NTT ~ "CONFLICT (Both TT and NTT)",
      TT ~ "Tenure-Track/Tenured",
      NTT ~ "Non-Tenure-Track",
      TRUE ~ "Unclassified"
    )
  ) %>%
  count(Classification, PositionType) %>%
  arrange(Classification, desc(n))

tenure_check %>%
  kable(caption = "Tenure Track Classification Check") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

# Flag any conflicts
conflicts <- tenure_check %>%
  filter(str_detect(Classification, "CONFLICT"))

if (nrow(conflicts) > 0) {
  cat("\n🚨 ERROR: Some positions are classified as BOTH TT and NTT!\n")
  cat("This should not happen. Check the classification logic.\n")
}

# Show unclassified
unclassified <- tenure_check %>%
  filter(Classification == "Unclassified")

if (nrow(unclassified) > 0) {
  cat("\n⚠️ NOTE:", sum(unclassified$n), "positions could not be classified as TT or NTT.\n")
  cat("These will be excluded from TT vs. NTT comparisons.\n")
  print(unclassified)
}
```

### Sample Sizes for Salary Tables

```{r salary-table-cell-sizes}
# Check cell sizes for salary tables (explaining the blanks)
cell_sizes <- dat_simple %>%
  filter(!is.na(GrossSalary), !is.na(RankGrp), !is.na(FullPart)) %>%
  count(RankGrp, FullPart) %>%
  pivot_wider(names_from = FullPart, values_from = n, values_fill = 0) %>%
  mutate(
    `Full-time` = ifelse(`Full-time` < 3, paste0(`Full-time`, " ⚠️"), as.character(`Full-time`)),
    `Part-time` = ifelse(`Part-time` < 3, paste0(`Part-time`, " ⚠️"), as.character(`Part-time`))
  )

cell_sizes %>%
  kable(caption = "Cell Sizes for Salary Tables (⚠️ = suppressed due to n<3)") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

cat("\nCells marked with ⚠️ will show as '—' in salary tables due to privacy protection (n < 3).\n")
```

# Sample Demographics

## Membership Status

```{r membership}
mem_status <- dat %>%
  count(MemStatus) %>%
  mutate(
    Percentage = round(100 * n / sum(n), 1),
    Label = paste0(n, " (", Percentage, "%)")
  )

mem_status %>%
  kable(caption = "Sample Membership Status") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```

## Professional Degree

```{r degree}
deg_summary <- dat %>%
  count(ProfDeg) %>%
  mutate(Percentage = round(100 * n / sum(n), 1)) %>%
  arrange(desc(n))

ggplot(deg_summary, aes(x = reorder(ProfDeg, n), y = Percentage, fill = ProfDeg)) +
  geom_col(show.legend = FALSE) +
  geom_text(aes(label = paste0(n, " (", Percentage, "%)")), hjust = -0.2, size = 4) +
  coord_flip() +
  scale_y_continuous(limits = c(0, 100), breaks = seq(0, 100, 20)) +
  scale_fill_manual(values = aptc_palette) +
  labs(title = "Professional Degrees", x = NULL, y = "Percentage (%)") +
  theme_minimal(base_size = 13) +
  theme(
    plot.title = element_text(face = "bold", color = aptc_navy),
    panel.grid.minor = element_blank()
  )
```

## Degree Area

```{r degree-area}
deg_area <- dat %>%
  count(DegArea) %>%
  mutate(Percentage = round(100 * n / sum(n), 1)) %>%
  arrange(desc(n))

ggplot(deg_area, aes(x = reorder(DegArea, n), y = Percentage, fill = DegArea)) +
  geom_col(show.legend = FALSE) +
  geom_text(aes(label = paste0(n, " (", Percentage, "%)")), hjust = -0.2, size = 4) +
  coord_flip() +
  scale_y_continuous(limits = c(0, 100), breaks = seq(0, 100, 20)) +
  scale_fill_manual(values = aptc_palette) +
  labs(title = "Graduate Degree Areas", x = NULL, y = "Percentage (%)") +
  theme_minimal(base_size = 13) +
  theme(
    plot.title = element_text(face = "bold", color = aptc_navy),
    panel.grid.minor = element_blank()
  )
```

## Role Duration

```{r role-duration}
role_stats <- dat %>%
  filter(!is.na(RoleDuration), RoleDuration >= 0) %>%
  summarise(
    N = n(),
    Mean = mean(RoleDuration, na.rm = TRUE),
    SD = sd(RoleDuration, na.rm = TRUE),
    Median = median(RoleDuration, na.rm = TRUE),
    Mode = as.numeric(names(sort(table(RoleDuration), decreasing = TRUE)[1])),
    Min = min(RoleDuration, na.rm = TRUE),
    Max = max(RoleDuration, na.rm = TRUE)
  )

dat %>%
  filter(!is.na(RoleDuration), RoleDuration >= 0) %>%
  ggplot(aes(x = RoleDuration)) +
  geom_histogram(binwidth = 2, fill = aptc_teal, color = "white", alpha = 0.9) +
  geom_vline(aes(xintercept = median(RoleDuration)), color = aptc_coral, linetype = "dashed", size = 1) +
  labs(
    title = "How Long Have Directors Been in Their Role?",
    subtitle = paste0("Mean = ", round(role_stats$Mean, 2), " years | Median = ", role_stats$Median, " years"),
    x = "Years in Role", y = "Count"
  ) +
  theme_minimal(base_size = 13) +
  theme(
    plot.title = element_text(face = "bold", color = aptc_navy)
  )

role_stats %>%
  kable(digits = 2) %>%
  kable_styling()
```

# Position Characteristics

## Academic Rank by Tenure Status

```{r rank-tenure}
rank_tenure <- dat %>%
  filter(!is.na(Rank), !is.na(PositionType)) %>%
  mutate(
    Rank_clean = case_when(
      str_detect(Rank, regex("Assistant", ignore_case = TRUE)) ~ "Assistant Professor",
      str_detect(Rank, regex("Associate", ignore_case = TRUE)) ~ "Associate Professor",
      str_detect(Rank, regex("Full", ignore_case = TRUE)) ~ "Full Professor",
      TRUE ~ "Other"
    ),
    TenureStatus = case_when(
      is_tt(PositionType) ~ "TT/Tenured",
      is_ntt(PositionType) ~ "NTT",
      TRUE ~ "Other"
    )
  ) %>%
  count(Rank_clean, TenureStatus) %>%
  pivot_wider(names_from = TenureStatus, values_from = n, values_fill = 0)

rank_tenure %>%
  kable(caption = "Academic Rank by Tenure Status") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```

## Supervisor

```{r supervisor}
sup_summary <- dat %>%
  count(Supervisor) %>%
  mutate(Percentage = round(100 * n / sum(n), 1)) %>%
  arrange(desc(n))

ggplot(sup_summary, aes(x = reorder(Supervisor, n), y = Percentage, fill = Supervisor)) +
  geom_col(show.legend = FALSE) +
  geom_text(aes(label = paste0(n, " (", Percentage, "%)")), hjust = -0.2, size = 3.5) +
  coord_flip() +
  scale_y_continuous(limits = c(0, 100), breaks = seq(0, 100, 20)) +
  scale_fill_manual(values = aptc_palette) +
  labs(title = "To Whom Do Clinic Directors Report?", x = NULL, y = "Percentage (%)") +
  theme_minimal(base_size = 13) +
  theme(
    plot.title = element_text(face = "bold", color = aptc_navy),
    panel.grid.minor = element_blank()
  )
```

## Contract Characteristics

```{r contracts}
# Contract months
contract_months <- dat %>%
  count(ContractMonths) %>%
  mutate(Percentage = round(100 * n / sum(n), 1)) %>%
  arrange(desc(n))

# Contract length
contract_length <- dat %>%
  count(ContractLength) %>%
  mutate(Percentage = round(100 * n / sum(n), 1)) %>%
  arrange(desc(n))

p1 <- ggplot(contract_months, aes(x = reorder(ContractMonths, n), y = Percentage, fill = ContractMonths)) +
  geom_col(show.legend = FALSE) +
  geom_text(aes(label = paste0(n, " (", Percentage, "%)")), hjust = -0.2, size = 3) +
  coord_flip() +
  scale_y_continuous(limits = c(0, 100), breaks = seq(0, 100, 20)) +
  scale_fill_manual(values = aptc_palette) +
  labs(title = "Contract Type (Months)", x = NULL, y = "Percentage (%)") +
  theme_minimal(base_size = 11) +
  theme(plot.title = element_text(face = "bold", color = aptc_navy))

p2 <- ggplot(contract_length, aes(x = reorder(ContractLength, n), y = Percentage, fill = ContractLength)) +
  geom_col(show.legend = FALSE) +
  geom_text(aes(label = paste0(n, " (", Percentage, "%)")), hjust = -0.2, size = 3) +
  coord_flip() +
  scale_y_continuous(limits = c(0, 100), breaks = seq(0, 100, 20)) +
  scale_fill_manual(values = aptc_palette) +
  labs(title = "Contract Length", x = NULL, y = "Percentage (%)") +
  theme_minimal(base_size = 11) +
  theme(plot.title = element_text(face = "bold", color = aptc_navy))

p1 + p2
```

# Salary Analysis

## Overall Salary Distribution

```{r salary-overall}
salary_stats <- dat_simple %>%
  filter(!is.na(GrossSalary)) %>%
  summarise(
    N = n(),
    Mean = mean(GrossSalary),
    SD = sd(GrossSalary),
    Median = median(GrossSalary),
    Q1 = quantile(GrossSalary, 0.25),
    Q3 = quantile(GrossSalary, 0.75),
    Min = min(GrossSalary),
    Max = max(GrossSalary)
  )

dat_simple %>%
  filter(!is.na(GrossSalary)) %>%
  ggplot(aes(x = GrossSalary)) +
  geom_histogram(binwidth = 10000, fill = aptc_teal, color = "white", alpha = 0.9) +
  geom_vline(aes(xintercept = median(GrossSalary)), color = aptc_coral, linetype = "dashed", size = 1) +
  scale_x_continuous(labels = dollar_format()) +
  labs(
    title = "Gross Salary Distribution",
    subtitle = paste0("Median = ", dollar(salary_stats$Median), " | Mean = ", dollar(salary_stats$Mean)),
    x = "Gross Salary", y = "Count"
  ) +
  theme_minimal(base_size = 13) +
  theme(
    plot.title = element_text(face = "bold", color = aptc_navy)
  )

salary_stats %>%
  mutate(across(where(is.numeric), ~dollar(.))) %>%
  kable() %>%
  kable_styling()
```

## Salary by Rank and Full-Time/Part-Time

```{r salary-tables}
# Function to make salary table
make_salary_table <- function(df) {
  df %>%
    filter(!is.na(GrossSalary), FullPart %in% c("Full-time", "Part-time")) %>%
    group_by(RankGrp, FullPart) %>%
    summarise(n = n(), avg = mean(GrossSalary), .groups = "drop") %>%
    mutate(val = ifelse(n >= 3, dollar(round(avg, 0)), "—")) %>%
    select(RankGrp, FullPart, val) %>%
    complete(RankGrp, FullPart = c("Full-time", "Part-time")) %>%
    pivot_wider(
      names_from = FullPart,
      values_from = val,
      names_glue = "Avg. {FullPart} Salary"
    ) %>%
    group_by(RankGrp) %>%
    summarise(
      `Avg. Full-time Salary` = first(na.omit(`Avg. Full-time Salary`)),
      `Avg. Part-time Salary` = first(na.omit(`Avg. Part-time Salary`)),
      .groups = "drop"
    ) %>%
    mutate(
      `Avg. Full-Time Salary` = ifelse(is.na(`Avg. Full-time Salary`), "—", `Avg. Full-time Salary`),
      `Avg. Part-Time Salary*` = ifelse(is.na(`Avg. Part-time Salary`), "—", `Avg. Part-time Salary`)
    ) %>%
    select(`Rank / Role` = RankGrp, `Avg. Full-Time Salary`, `Avg. Part-Time Salary*`) %>%
    arrange(`Rank / Role`)
}

# Overall table
overall_table <- make_salary_table(dat_simple)

overall_table %>%
  gt() %>%
  tab_header(
    title = md("**Average Faculty Salaries – All Positions**"),
    subtitle = "Full-time and Part-time Averages (suppressed if n < 3)"
  ) %>%
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_column_labels(everything())
  ) %>%
  tab_source_note(
    source_note = md("*Cells suppressed when based on fewer than 3 respondents*")
  )
```

### Tenure-Track/Tenured Positions

```{r salary-tt}
tt_table <- dat_simple %>% 
  filter(is_tt(PositionType)) %>% 
  make_salary_table()

tt_table %>%
  gt() %>%
  tab_header(
    title = md("**Average Faculty Salaries – Tenure/Tenure-Track (TT)**"),
    subtitle = "Full-time and Part-time Averages (suppressed if n < 3)"
  ) %>%
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_column_labels(everything())
  ) %>%
  tab_source_note(
    source_note = md("*Cells suppressed when based on fewer than 3 respondents*")
  )
```

### Non-Tenure-Track Positions

```{r salary-ntt}
ntt_table <- dat_simple %>% 
  filter(is_ntt(PositionType)) %>% 
  make_salary_table()

ntt_table %>%
  gt() %>%
  tab_header(
    title = md("**Average Faculty Salaries – Non-Tenure-Track (NTT)**"),
    subtitle = "Full-time and Part-time Averages (suppressed if n < 3)"
  ) %>%
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_column_labels(everything())
  ) %>%
  tab_source_note(
    source_note = md("*Cells suppressed when based on fewer than 3 respondents*")
  )
```

## Salary by Contract Type

```{r salary-contract}
dat_simple %>%
  filter(!is.na(GrossSalary), !is.na(ContractLength)) %>%
  ggplot(aes(x = reorder(ContractLength, GrossSalary, median), y = GrossSalary, fill = ContractLength)) +
  geom_boxplot(alpha = 0.8, show.legend = FALSE) +
  coord_flip() +
  scale_y_continuous(labels = dollar_format()) +
  scale_fill_manual(values = aptc_palette) +
  labs(title = "Salary by Contract Length", x = "Contract Length", y = "Gross Salary") +
  theme_minimal(base_size = 13) +
  theme(
    plot.title = element_text(face = "bold", color = aptc_navy)
  )
```

**Note on Salary Tables:** The salary tables above show "—" (blank) cells when there are **fewer than 3 respondents** in that category. This is a privacy protection measure to prevent identification of individuals. For example, if only 1-2 part-time full professors responded, their average salary is suppressed.

## Professional Development Funding

```{r pd-funding}
pd_summary <- dat %>%
  count(PDFunds) %>%
  mutate(Percentage = round(100 * n / sum(n), 1)) %>%
  arrange(desc(n))

pd_summary %>%
  kable(caption = "Professional Development Funding") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```

# Responsibilities and Workload

## Hours Worked in Clinic

```{r hours-clinic}
hours_stats <- dat %>%
  filter(!is.na(HoursWorkClinic)) %>%
  summarise(
    N = n(),
    Mean = mean(HoursWorkClinic),
    SD = sd(HoursWorkClinic),
    Median = median(HoursWorkClinic),
    Min = min(HoursWorkClinic),
    Max = max(HoursWorkClinic)
  )

dat %>%
  filter(!is.na(HoursWorkClinic)) %>%
  ggplot(aes(x = HoursWorkClinic)) +
  geom_histogram(binwidth = 5, fill = aptc_teal, color = "white", alpha = 0.9) +
  geom_vline(aes(xintercept = median(HoursWorkClinic)), color = aptc_coral, linetype = "dashed", size = 1) +
  labs(
    title = "Hours Per Week Spent on Clinic Activities",
    subtitle = paste0("Median = ", hours_stats$Median, " hours | Mean = ", round(hours_stats$Mean, 1), " hours"),
    x = "Hours per Week", y = "Count"
  ) +
  theme_minimal(base_size = 13) +
  theme(
    plot.title = element_text(face = "bold", color = aptc_navy)
  )
```

## Teaching

```{r teaching}
teaching_summary <- dat %>%
  count(TeachingBinary) %>%
  mutate(Percentage = round(100 * n / sum(n), 1))

courses_summary <- dat %>%
  filter(TeachingBinary == "Yes", !is.na(CoursesTaught)) %>%
  summarise(
    N = n(),
    Mean = mean(CoursesTaught),
    Median = median(CoursesTaught),
    Min = min(CoursesTaught),
    Max = max(CoursesTaught)
  )

p1 <- ggplot(teaching_summary, aes(x = TeachingBinary, y = Percentage, fill = TeachingBinary)) +
  geom_col(show.legend = FALSE) +
  geom_text(aes(label = paste0(n, "\n(", Percentage, "%)")), vjust = -0.5, size = 4) +
  scale_y_continuous(limits = c(0, 100), breaks = seq(0, 100, 20)) +
  scale_fill_manual(values = c("Yes" = aptc_teal, "No" = aptc_coral)) +
  labs(title = "Do Directors Teach?", x = NULL, y = "Percentage (%)") +
  theme_minimal(base_size = 12) +
  theme(plot.title = element_text(face = "bold", color = aptc_navy))

p2 <- dat %>%
  filter(TeachingBinary == "Yes", !is.na(CoursesTaught)) %>%
  ggplot(aes(x = CoursesTaught)) +
  geom_histogram(binwidth = 1, fill = aptc_teal, color = "white", alpha = 0.9) +
  labs(
    title = "Courses Taught per Year",
    subtitle = paste0("Among those who teach (n=", courses_summary$N, ")"),
    x = "Number of Courses", y = "Count"
  ) +
  theme_minimal(base_size = 12) +
  theme(plot.title = element_text(face = "bold", color = aptc_navy))

p1 + p2
```

# Clinic Characteristics

## Training Model and Clinic Age

```{r clinic-model}
model_summary <- dat %>%
  count(ClinicTrainingModel) %>%
  mutate(Percentage = round(100 * n / sum(n), 1)) %>%
  arrange(desc(n))

age_stats <- dat %>%
  filter(!is.na(ClinicAge), ClinicAge >= 0) %>%
  summarise(
    N = n(),
    Mean = mean(ClinicAge),
    SD = sd(ClinicAge),
    Median = median(ClinicAge),
    Min = min(ClinicAge),
    Max = max(ClinicAge)
  )

p1 <- ggplot(model_summary, aes(x = reorder(ClinicTrainingModel, n), y = Percentage, fill = ClinicTrainingModel)) +
  geom_col(show.legend = FALSE) +
  geom_text(aes(label = paste0(n, "\n(", Percentage, "%)")), hjust = -0.2, size = 3) +
  coord_flip() +
  scale_y_continuous(limits = c(0, 100), breaks = seq(0, 100, 20)) +
  scale_fill_manual(values = aptc_palette) +
  labs(title = "Training Model", x = NULL, y = "Percentage (%)") +
  theme_minimal(base_size = 11) +
  theme(plot.title = element_text(face = "bold", color = aptc_navy))

p2 <- dat %>%
  filter(!is.na(ClinicAge), ClinicAge >= 0) %>%
  ggplot(aes(x = ClinicAge)) +
  geom_histogram(binwidth = 10, fill = aptc_coral, color = "white", alpha = 0.9) +
  geom_vline(aes(xintercept = median(ClinicAge)), color = aptc_navy, linetype = "dashed", size = 1) +
  labs(
    title = "Clinic Age (Years)",
    subtitle = paste0("Mean = ", round(age_stats$Mean, 1), " | Median = ", age_stats$Median),
    x = "Years", y = "Count"
  ) +
  theme_minimal(base_size = 11) +
  theme(plot.title = element_text(face = "bold", color = aptc_navy))

p1 + p2
```

## Trainees and Clients

```{r trainees-clients}
trainee_stats <- dat %>%
  filter(!is.na(ClinicTotalTrainees), ClinicTotalTrainees > 0) %>%
  summarise(
    N = n(),
    Mean = mean(ClinicTotalTrainees),
    SD = sd(ClinicTotalTrainees),
    Median = median(ClinicTotalTrainees),
    Min = min(ClinicTotalTrainees),
    Max = max(ClinicTotalTrainees)
  )

client_stats <- dat %>%
  filter(!is.na(ClinicClientsCount), ClinicClientsCount > 0) %>%
  summarise(
    N = n(),
    Mean = mean(ClinicClientsCount),
    SD = sd(ClinicClientsCount),
    Median = median(ClinicClientsCount),
    Min = min(ClinicClientsCount),
    Max = max(ClinicClientsCount)
  )

p1 <- dat %>%
  filter(!is.na(ClinicTotalTrainees), ClinicTotalTrainees > 0) %>%
  ggplot(aes(x = ClinicTotalTrainees)) +
  geom_histogram(binwidth = 5, fill = aptc_teal, color = "white", alpha = 0.9) +
  geom_vline(aes(xintercept = median(ClinicTotalTrainees)), color = aptc_coral, linetype = "dashed", size = 1) +
  labs(
    title = "Trainees per Year",
    subtitle = paste0("Mean = ", round(trainee_stats$Mean, 1), " | Median = ", trainee_stats$Median),
    x = "Number of Trainees", y = "Count"
  ) +
  theme_minimal(base_size = 11) +
  theme(plot.title = element_text(face = "bold", color = aptc_navy))

p2 <- dat %>%
  filter(!is.na(ClinicClientsCount), ClinicClientsCount > 0) %>%
  ggplot(aes(x = ClinicClientsCount)) +
  geom_histogram(binwidth = 25, fill = aptc_coral, color = "white", alpha = 0.9) +
  geom_vline(aes(xintercept = median(ClinicClientsCount)), color = aptc_navy, linetype = "dashed", size = 1) +
  labs(
    title = "Clients per Year",
    subtitle = paste0("Mean = ", round(client_stats$Mean, 1), " | Median = ", client_stats$Median),
    x = "Number of Clients", y = "Count"
  ) +
  theme_minimal(base_size = 11) +
  theme(plot.title = element_text(face = "bold", color = aptc_navy))

p1 + p2
```

## Clinic Services

```{r services}
# Therapy services
therapy_binary <- dat %>%
  count(ClinicTherapyBinary) %>%
  mutate(Percentage = round(100 * n / sum(n), 1))

# Assessment services
assmnt_binary <- dat %>%
  count(ClinicAssmntBinary) %>%
  mutate(Percentage = round(100 * n / sum(n), 1))

therapy_binary %>%
  kable(caption = "Clinics Offering Therapy Services") %>%
  kable_styling()

assmnt_binary %>%
  kable(caption = "Clinics Offering Assessment Services") %>%
  kable_styling()
```

# Financial Information

## Sliding Scale

```{r sliding-scale}
sliding_scale <- dat %>%
  count(ClinicSlidingScale) %>%
  mutate(Percentage = round(100 * n / sum(n), 1))

ggplot(sliding_scale, aes(x = ClinicSlidingScale, y = Percentage, fill = ClinicSlidingScale)) +
  geom_col(show.legend = FALSE) +
  geom_text(aes(label = paste0(n, " (", Percentage, "%)")), vjust = -0.5, size = 5) +
  scale_y_continuous(limits = c(0, 100), breaks = seq(0, 100, 20)) +
  scale_fill_manual(values = c("Yes" = aptc_teal, "No" = aptc_coral)) +
  labs(title = "Do Clinics Offer a Sliding Scale?", x = NULL, y = "Percentage (%)") +
  theme_minimal(base_size = 13) +
  theme(plot.title = element_text(face = "bold", color = aptc_navy))
```

## Clinic Revenue

```{r revenue}
revenue_stats <- dat %>%
  filter(!is.na(ClinicRevenue), ClinicRevenue > 0) %>%
  summarise(
    N = n(),
    Mean = mean(ClinicRevenue),
    SD = sd(ClinicRevenue),
    Median = median(ClinicRevenue),
    Q1 = quantile(ClinicRevenue, 0.25),
    Q3 = quantile(ClinicRevenue, 0.75),
    Min = min(ClinicRevenue),
    Max = max(ClinicRevenue)
  )

dat %>%
  filter(!is.na(ClinicRevenue), ClinicRevenue > 0, ClinicRevenue < 500000) %>%
  ggplot(aes(x = ClinicRevenue)) +
  geom_histogram(binwidth = 25000, fill = aptc_teal, color = "white", alpha = 0.9) +
  geom_vline(aes(xintercept = median(ClinicRevenue, na.rm = TRUE)), color = aptc_coral, linetype = "dashed", size = 1) +
  scale_x_continuous(labels = dollar_format()) +
  labs(
    title = "Annual Clinic Revenue Distribution",
    subtitle = paste0("Median = ", dollar(revenue_stats$Median), " | Mean = ", dollar(revenue_stats$Mean)),
    x = "Annual Revenue", y = "Count"
  ) +
  theme_minimal(base_size = 13) +
  theme(
    plot.title = element_text(face = "bold", color = aptc_navy)
  )
```

## Revenue by Client Count

```{r revenue-clients}
dat_revenue <- dat %>%
  filter(!is.na(ClinicRevenue), !is.na(ClinicClientsCount),
         ClinicRevenue > 0, ClinicClientsCount > 0,
         ClinicRevenue < 1000000) %>%
  mutate(
    ClinicSize = case_when(
      ClinicClientsCount < 93 ~ "Small (<93)",
      ClinicClientsCount >= 93 & ClinicClientsCount <= 130 ~ "Medium (93-130)",
      ClinicClientsCount > 130 ~ "Large (>130)"
    ),
    ClinicSize = factor(ClinicSize, levels = c("Small (<93)", "Medium (93-130)", "Large (>130)"))
  )

# Correlation
cor_result <- cor.test(dat_revenue$ClinicClientsCount, dat_revenue$ClinicRevenue)

ggplot(dat_revenue, aes(x = ClinicClientsCount, y = ClinicRevenue, color = ClinicSize)) +
  geom_point(size = 3, alpha = 0.7) +
  geom_smooth(method = "lm", se = TRUE, color = aptc_navy, linetype = "dashed") +
  scale_y_continuous(labels = dollar_format()) +
  scale_color_manual(values = c("Small (<93)" = aptc_coral, 
                                 "Medium (93-130)" = aptc_teal, 
                                 "Large (>130)" = aptc_navy)) +
  labs(
    title = "Clinic Revenue by Client Number",
    subtitle = paste0("Correlation: r = ", round(cor_result$estimate, 2)),
    x = "Number of Clients per Year",
    y = "Annual Clinic Revenue",
    color = "Clinic Size"
  ) +
  theme_minimal(base_size = 13) +
  theme(
    plot.title = element_text(face = "bold", color = aptc_navy),
    legend.position = "top"
  )
```

# Staff and Operations

## Number of Rooms

```{r rooms}
room_stats <- dat %>%
  filter(!is.na(NumRooms), NumRooms > 0) %>%
  summarise(
    N = n(),
    Mean = mean(NumRooms),
    SD = sd(NumRooms),
    Median = median(NumRooms),
    Min = min(NumRooms),
    Max = max(NumRooms)
  )

dat %>%
  filter(!is.na(NumRooms), NumRooms > 0) %>%
  ggplot(aes(x = NumRooms)) +
  geom_histogram(binwidth = 2, fill = aptc_teal, color = "white", alpha = 0.9) +
  geom_vline(aes(xintercept = median(NumRooms)), color = aptc_coral, linetype = "dashed", size = 1) +
  labs(
    title = "Number of Clinic Rooms",
    subtitle = paste0("Mean = ", round(room_stats$Mean, 1), " | Median = ", room_stats$Median),
    x = "Number of Rooms", y = "Count"
  ) +
  theme_minimal(base_size = 13) +
  theme(
    plot.title = element_text(face = "bold", color = aptc_navy)
  )
```

## Supervisors and Caseloads

```{r supervisors}
max_trainee_summary <- dat %>%
  filter(!is.na(MaxTraineeCount), MaxTraineeCount > 0) %>%
  summarise(
    N = n(),
    Mean = mean(MaxTraineeCount),
    SD = sd(MaxTraineeCount),
    Median = median(MaxTraineeCount),
    Min = min(MaxTraineeCount),
    Max = max(MaxTraineeCount)
  )

dat %>%
  filter(!is.na(MaxTraineeCount), MaxTraineeCount > 0) %>%
  ggplot(aes(x = MaxTraineeCount)) +
  geom_histogram(binwidth = 2, fill = aptc_coral, color = "white", alpha = 0.9) +
  geom_vline(aes(xintercept = median(MaxTraineeCount)), color = aptc_navy, linetype = "dashed", size = 1) +
  labs(
    title = "Maximum Trainees per Supervisor",
    subtitle = paste0("Mean = ", round(max_trainee_summary$Mean, 1), " | Median = ", max_trainee_summary$Median),
    x = "Max Trainees", y = "Count"
  ) +
  theme_minimal(base_size = 13) +
  theme(
    plot.title = element_text(face = "bold", color = aptc_navy)
  )
```

# Technology

## EMR Usage

```{r emr}
emr_summary <- dat %>%
  count(EMRbinary) %>%
  mutate(Percentage = round(100 * n / sum(n), 1))

ggplot(emr_summary, aes(x = EMRbinary, y = Percentage, fill = EMRbinary)) +
  geom_col(show.legend = FALSE) +
  geom_text(aes(label = paste0(n, " (", Percentage, "%)")), vjust = -0.5, size = 5) +
  scale_y_continuous(limits = c(0, 100), breaks = seq(0, 100, 20)) +
  scale_fill_manual(values = c("Yes" = aptc_teal, "No" = aptc_coral)) +
  labs(title = "Electronic Medical Record (EMR) Usage", x = "Uses EMR?", y = "Percentage (%)") +
  theme_minimal(base_size = 13) +
  theme(plot.title = element_text(face = "bold", color = aptc_navy))
```

## Telehealth

```{r telehealth}
telehealth_summary <- dat %>%
  count(Telehealth) %>%
  mutate(Percentage = round(100 * n / sum(n), 1))

ggplot(telehealth_summary, aes(x = Telehealth, y = Percentage, fill = Telehealth)) +
  geom_col(show.legend = FALSE) +
  geom_text(aes(label = paste0(n, " (", Percentage, "%)")), vjust = -0.5, size = 5) +
  scale_y_continuous(limits = c(0, 100), breaks = seq(0, 100, 20)) +
  scale_fill_manual(values = c("Yes" = aptc_teal, "No" = aptc_coral)) +
  labs(title = "Telehealth Service Provision", x = "Offers Telehealth?", y = "Percentage (%)") +
  theme_minimal(base_size = 13) +
  theme(plot.title = element_text(face = "bold", color = aptc_navy))
```

## Artificial Intelligence

```{r ai}
ai_clindir <- dat %>%
  count(AIUseClinDir) %>%
  mutate(Percentage = round(100 * n / sum(n), 1))

ai_students <- dat %>%
  count(AIUseStudentsAllowed) %>%
  mutate(Percentage = round(100 * n / sum(n), 1))

p1 <- ggplot(ai_clindir, aes(x = AIUseClinDir, y = Percentage, fill = AIUseClinDir)) +
  geom_col(show.legend = FALSE) +
  geom_text(aes(label = paste0(Percentage, "%")), vjust = -0.5, size = 4) +
  scale_y_continuous(limits = c(0, 100), breaks = seq(0, 100, 20)) +
  scale_fill_manual(values = aptc_palette) +
  labs(title = "AI Use by Clinic Directors", x = NULL, y = "Percentage (%)") +
  theme_minimal(base_size = 11) +
  theme(plot.title = element_text(face = "bold", color = aptc_navy))

p2 <- ggplot(ai_students, aes(x = AIUseStudentsAllowed, y = Percentage, fill = AIUseStudentsAllowed)) +
  geom_col(show.legend = FALSE) +
  geom_text(aes(label = paste0(Percentage, "%")), vjust = -0.5, size = 4) +
  scale_y_continuous(limits = c(0, 100), breaks = seq(0, 100, 20)) +
  scale_fill_manual(values = aptc_palette) +
  labs(title = "AI Use Allowed for Students", x = NULL, y = "Percentage (%)") +
  theme_minimal(base_size = 11) +
  theme(
    plot.title = element_text(face = "bold", color = aptc_navy),
    axis.text.x = element_text(angle = 20, hjust = 1)
  )

p1 + p2
```

# Research Activities

```{r research}
research_summary <- dat %>%
  count(ResearchActive) %>%
  mutate(Percentage = round(100 * n / sum(n), 1))

ggplot(research_summary, aes(x = ResearchActive, y = Percentage, fill = ResearchActive)) +
  geom_col(show.legend = FALSE) +
  geom_text(aes(label = paste0(n, " (", Percentage, "%)")), vjust = -0.5, size = 4) +
  scale_y_continuous(limits = c(0, 100), breaks = seq(0, 100, 20)) +
  scale_fill_manual(values = aptc_palette) +
  labs(title = "Research Activity in Training Clinics", x = "Research Status", y = "Percentage (%)") +
  theme_minimal(base_size = 13) +
  theme(
    plot.title = element_text(face = "bold", color = aptc_navy),
    axis.text.x = element_text(angle = 15, hjust = 1)
  )
```

# Burnout and Job Satisfaction

## Burnout Levels

```{r burnout}
burnout_stats <- dat %>%
  filter(!is.na(Burnout_1)) %>%
  summarise(
    N = n(),
    Mean = mean(Burnout_1),
    SD = sd(Burnout_1),
    Median = median(Burnout_1),
    Min = min(Burnout_1),
    Max = max(Burnout_1)
  )

dat %>%
  filter(!is.na(Burnout_1)) %>%
  ggplot(aes(x = Burnout_1)) +
  geom_histogram(binwidth = 1, fill = aptc_coral, color = "white", alpha = 0.9) +
  geom_vline(aes(xintercept = mean(Burnout_1)), color = aptc_navy, linetype = "dashed", size = 1) +
  scale_x_continuous(breaks = 0:6) +
  labs(
    title = "Burnout Levels Among Clinic Directors",
    subtitle = paste0("Mean = ", round(burnout_stats$Mean, 2), " (SD = ", round(burnout_stats$SD, 2), ") | Range: 0-6"),
    x = "Burnout Score (0 = No burnout, 6 = Severe burnout)",
    y = "Count"
  ) +
  theme_minimal(base_size = 13) +
  theme(
    plot.title = element_text(face = "bold", color = aptc_navy)
  )
```

# Interpretation Guide

## Understanding the Data Quality Checks

The **Data Quality Checks** section at the beginning of this document runs automatically and shows you:

### 1. **Sample Size Verification**

-   How many people started vs. finished the survey
-   Your final analytic sample size
-   **Action:** If the numbers don't match expectations, investigate drop-out patterns

### 2. **Categorical Variable Values**

Shows the actual response options in your data for: - Membership status - Professional degrees - Teaching (Yes/No) - EMR usage - Position types

**Action:** If values look unexpected (e.g., "1" instead of "Yes"), you may need to recode variables

### 3. **Missing Data Summary**

Lists variables with missing data and completion rates.

**Interpretation:** - \<10% missing = Excellent - 10-20% missing = Good, but note in limitations - 20-50% missing = Problematic, consider whether results are representative - \>50% missing = Major concern, may not be usable

**Action:** For variables with high missing rates, add a note explaining why (e.g., "Only asked of those who teach")

### 4. **Salary Range Checks**

Shows min/max/median salaries and flags potential outliers.

**Look for:** - Salaries below \$30,000 (could be part-time or data entry errors) - Salaries above \$200,000 (verify these are accurate) - Impossible values (negative numbers, zero)

**Action:** Decide whether flagged values are real or should be excluded

### 5. **Revenue Range Checks**

Same concept as salary checks, but for clinic revenue.

**Look for:** - Revenues above \$1,000,000 (some visualizations exclude these) - Impossible values

**Action:** Decide on appropriate cutoffs for your data

### 6. **Tenure Classification Verification**

Shows how the automatic classification assigned positions to TT/NTT categories.

**Check for:** - 🚨 **Conflicts** (classified as both TT and NTT) - this is an error - ⚠️ **Unclassified** positions - won't appear in TT vs. NTT comparisons - Unexpected classifications - verify a sample manually

**Action:** If many positions are unclassified, you may need to adjust the classification rules

### 7. **Salary Table Cell Sizes**

Shows how many people are in each rank × employment type combination.

**Cells marked ⚠️** have fewer than 3 people and will show as "—" in salary tables.

**This is normal** - it's privacy protection, not a data problem.

## Recommendations Based on Your Data

After running the document, review the Data Quality Checks section and:

### ✅ **If Everything Looks Good:**

1.  Note the final sample size in your methods section
2.  Cite completion rates for key variables
3.  Use the document as-is for presentations/reports

### ⚠️ **If You Find Issues:**

**Issue: Unexpected response values** - Example: `TeachingBinary` shows "1" and "2" instead of "Yes" and "No" - **Fix:** Add recoding in the data loading section: `r   mutate(TeachingBinary = ifelse(TeachingBinary == "1", "Yes", "No"))`

**Issue: High missing data rates** - **Fix:** Add interpretation notes in relevant sections - Consider: Are missings systematic? (e.g., only NTT faculty skip certain questions) - May need to report "Of those who responded to this item (n=X)..."

**Issue: Outliers in salary/revenue** - **Fix:** Decide on defensible cutoffs - Document your decision (e.g., "One clinic reported revenue \>\$1M and was excluded as an outlier") - Or keep them but note them

**Issue: Many unclassified positions** - **Fix:** Expand the classification rules to capture more patterns - Or add manual classification for specific cases

**Issue: Small cell sizes in tables** - **Fix:** Consider collapsing categories (e.g., combine "Associate" and "Full" professors) - Or simply note that some combinations are too rare to report

## What This Document Provides

### ✅ **Strengths**

1.  **Automated quality checks** - You see problems immediately
2.  **Consistent APTC branding** - Ready for presentations
3.  **Comprehensive coverage** - All major survey domains
4.  **Privacy protection** - Automatic suppression of small cells
5.  **Reproducible** - Run anytime with updated data
6.  **Transparent** - Shows you exactly what's happening

### 📊 **What You Still Need to Do**

1.  **Review data quality output** and address any red flags
2.  **Verify tenure classifications** manually for a sample
3.  **Add interpretation** of findings in context
4.  **Note limitations** based on missing data
5.  **Add comparison** to prior years (if applicable)
6.  **Write discussion** of implications

## Next Steps

1.  **Run the document** with your real data
2.  **Review the Data Quality Checks section** carefully
3.  **Address any warnings or errors** that appear
4.  **Verify** that percentages and statistics make sense
5.  **Add context** to findings based on your knowledge
6.  **Share** with co-authors for review
7.  **Iterate** as needed

The document is designed to **show you** what's in your data and **flag potential issues** automatically, rather than just assuming everything is perfect.

# Session Information

```{r session}
sessionInfo()
```
