---
title: "APTC 2026 Survey Results"
subtitle: "Association of Psychology Training Clinics"
author: "Jacqueline Hersh, Ph.D. & Ryan L. Farmer, Ph.D."
date: today
format:
  revealjs:
    theme: [default, custom.scss]
    slide-number: true
    logo: ""
    footer: "APTC 2026 Annual Survey"
    transition: fade
    background-transition: fade
    highlight-style: github
    code-fold: true
    fig-width: 10
    fig-height: 6
editor: visual
execute:
  echo: false
  warning: false
  message: false
---

```{r setup, include=FALSE}
library(readxl)
library(tidyverse)
library(scales)
library(gt)
library(knitr)
library(kableExtra)

# APTC Colors
aptc_navy  <- "#252b3b"
aptc_coral <- "#ff6544"
aptc_teal  <- "#31a8c0"

aptc_palette <- c(
 aptc_coral, "#ff8f77", "#e24f33",
 aptc_teal, "#5bc0d4", "#1f7f92",
 aptc_navy, "#454d5f", "#161b29"
)

# Load and clean data (same as analysis)
dat <- read_excel("dat.xlsx")
dat <- dat[-1, ]

dat <- dat %>%
 mutate(across(where(is.numeric), ~ na_if(., -99))) %>%
 mutate(across(where(is.character), ~ na_if(., "-99"))) %>%
 mutate(
   across(
     matches("Binary$"),
     ~ case_when(
       str_detect(., regex("^yes$", ignore_case = TRUE)) ~ "Yes",
       str_detect(., regex("^no$",  ignore_case = TRUE)) ~ "No",
       TRUE ~ NA_character_
     )
   )
 ) %>%
 mutate(
   Progress = as.numeric(Progress),
   GrossSalary = as.numeric(GrossSalary),
   FTESalary = as.numeric(FTESalary),
   RoleDuration = as.numeric(RoleDuration),
   ClinicDuration = as.numeric(ClinicDuration),
   ClinicAge = as.numeric(ClinicAge),
   HoursWorkClinic = as.numeric(HoursWorkClinic),
   CoursesTaught = as.numeric(CoursesTaught),
   ClinicTotalTrainees = as.numeric(ClinicTotalTrainees),
   ClinicClientsCount = as.numeric(ClinicClientsCount),
   NumRooms = as.numeric(NumRooms),
   MaxTraineeCount = as.numeric(MaxTraineeCount),
   ClinicRevenue = as.numeric(ClinicRevenue),
   Burnout_1 = as.numeric(Burnout_1),
   Burnout_2 = as.numeric(Burnout_2),
   Burnout_3 = as.numeric(Burnout_3),
   Burnout_4 = as.numeric(Burnout_4),
   Burnout_5 = as.numeric(Burnout_5),
   FTESupportStaff = as.numeric(FTESupportStaff),
   FTEGradStaff = as.numeric(FTEGradStaff),
   PostdocCount = as.numeric(PostdocCount),
   ClinicHours = as.numeric(ClinicHours),
   MaxTraineesTherapy = as.numeric(MaxTraineesTherapy),
   MaxTraineesAssmnt = as.numeric(MaxTraineesAssmnt),
   TxLength = as.numeric(TxLength),
   MaxTxCasesAllow = as.numeric(MaxTxCasesAllow),
   MaxAxCasesAllow = as.numeric(MaxAxCasesAllow)
 )

# Clean ClinSqFt as categorical
dat <- dat %>%
 mutate(
   ClinSqFt = case_when(
     ClinSqFt == "-99" ~ NA_character_,
     TRUE ~ ClinSqFt
   ),
   ClinSqFt = factor(ClinSqFt, levels = c(
     "Under 500 sq ft", "500–999 sq ft", "1,000–1,999 sq ft",
     "2,000–4,999 sq ft", "5,000 sq ft or more"
   ))
 )

# Rank grouping
dat <- dat %>%
 mutate(RankGrp = case_when(
   str_detect(Rank, regex("assistant", ignore_case = TRUE)) ~ "Assistant Professor",
   str_detect(Rank, regex("associate", ignore_case = TRUE)) ~ "Associate Professor",
   str_detect(Rank, regex("^full|full professor", ignore_case = TRUE)) ~ "Full Professor",
   str_detect(Rank, regex("lecturer|instructor", ignore_case = TRUE)) ~ "Lecturer",
   str_detect(Rank, regex("staff|n/a|not applicable", ignore_case = TRUE)) ~ "Staff (N/A)",
   !is.na(Rank) ~ "Other (specified)",
   TRUE ~ "Unspecified Rank"
 ))
```

# Sample Overview {background-color="#252b3b"}

::: notes
Welcome to the 2026 APTC Annual Survey results. This presentation covers key findings from our membership survey, including sample demographics, salary data, clinic operations, and director wellbeing.
:::

## Who Responded?

:::::: columns
::: {.column width="50%"}
```{r}
mem_status <- dat %>%
 count(MemStatus) %>%
 mutate(Percentage = round(100 * n / sum(n), 1))

ggplot(mem_status %>% filter(!is.na(MemStatus)), 
      aes(x = reorder(MemStatus, n), y = n, fill = MemStatus)) +
 geom_col(show.legend = FALSE) +
 geom_text(aes(label = paste0(n, " (", Percentage, "%)")), hjust = -0.1, size = 5) +
 coord_flip() +
 scale_fill_manual(values = aptc_palette) +
 scale_y_continuous(limits = c(0, 140)) +
 labs(title = "Membership Status", x = NULL, y = "Count") +
 theme_minimal(base_size = 16) +
 theme(plot.title = element_text(face = "bold", color = aptc_navy))
```
:::

:::: {.column width="50%"}
### Sample Highlights

-   **N = `r nrow(dat)`** total respondents
-   **`r sum(dat$MemStatus == "Member", na.rm = TRUE)`** full members (`r round(100*sum(dat$MemStatus == "Member", na.rm = TRUE)/nrow(dat), 1)`%)
-   **`r sum(dat$MemStatus == "Associate Member", na.rm = TRUE)`** associate members

::: callout-note
Throughout this presentation, n's vary because not everyone answered every question.
:::
::::
::::::

::: notes
Our sample includes 120 respondents, with 92% being full APTC members. Sample sizes vary across analyses due to item-level missingness.
:::

## Professional Background

```{r}
prof_deg <- dat %>%
 filter(!is.na(ProfDeg)) %>%
 count(ProfDeg) %>%
 mutate(Percentage = round(100 * n / sum(n), 1)) %>%
 arrange(desc(n))

ggplot(prof_deg, aes(x = reorder(ProfDeg, n), y = Percentage, fill = ProfDeg)) +
 geom_col(show.legend = FALSE) +
 geom_text(aes(label = paste0(n, " (", Percentage, "%)")), hjust = -0.1, size = 5) +
 coord_flip() +
 scale_fill_manual(values = aptc_palette) +
 scale_y_continuous(limits = c(0, 100)) +
 labs(title = "Professional Degree", x = NULL, y = "Percentage (%)") +
 theme_minimal(base_size = 16) +
 theme(plot.title = element_text(face = "bold", color = aptc_navy))
```

::: notes
The vast majority of clinic directors hold doctoral degrees in psychology, with Ph.D. being the most common credential.
:::

## Experience in Role

::::: columns
::: {.column width="50%"}
```{r}
role_stats <- dat %>%
 filter(!is.na(RoleDuration)) %>%
 summarise(N = n(), Mean = mean(RoleDuration), SD = sd(RoleDuration),
           Median = median(RoleDuration), Min = min(RoleDuration), Max = max(RoleDuration))

dat %>%
 filter(!is.na(RoleDuration)) %>%
 ggplot(aes(x = RoleDuration)) +
 geom_histogram(binwidth = 2, fill = aptc_teal, color = "white", alpha = 0.9) +
 geom_vline(aes(xintercept = median(RoleDuration)), color = aptc_coral, 
            linetype = "dashed", linewidth = 1.2) +
 labs(title = "Years in Current Role",
      subtitle = paste0("Median = ", role_stats$Median, " years"),
      x = "Years", y = "Count") +
 theme_minimal(base_size = 16) +
 theme(plot.title = element_text(face = "bold", color = aptc_navy))
```
:::

::: {.column width="50%"}
### Role Duration

| Statistic | Value                                         |
|-----------|-----------------------------------------------|
| N         | `r role_stats$N`                              |
| Mean      | `r round(role_stats$Mean, 1)` years           |
| Median    | `r role_stats$Median` years                   |
| Range     | `r role_stats$Min` – `r role_stats$Max` years |
:::
:::::

::: notes
Directors have a median of X years in their current role, with a wide range reflecting both new directors and long-tenured leaders.
:::

# Position Characteristics {background-color="#252b3b"}

## Academic Rank

```{r}
rank_summary <- dat %>%
 filter(!is.na(RankGrp)) %>%
 count(RankGrp) %>%
 mutate(Percentage = round(100 * n / sum(n), 1)) %>%
 arrange(desc(n))

ggplot(rank_summary, aes(x = reorder(RankGrp, n), y = Percentage, fill = RankGrp)) +
 geom_col(show.legend = FALSE) +
 geom_text(aes(label = paste0(n, " (", Percentage, "%)")), hjust = -0.1, size = 5) +
 coord_flip() +
 scale_fill_manual(values = aptc_palette) +
 scale_y_continuous(limits = c(0, 50)) +
 labs(title = "Academic Rank Distribution", x = NULL, y = "Percentage (%)") +
 theme_minimal(base_size = 16) +
 theme(plot.title = element_text(face = "bold", color = aptc_navy))
```

::: notes
Associate and Assistant Professor ranks are most common among clinic directors. A notable proportion hold staff positions without faculty rank.
:::

## Contract Characteristics

```{r}
contract_summary <- dat %>%
 filter(!is.na(ContractLength)) %>%
 count(ContractLength) %>%
 mutate(Percentage = round(100 * n / sum(n), 1)) %>%
 arrange(desc(n))

ggplot(contract_summary, aes(x = reorder(ContractLength, n), y = Percentage, fill = ContractLength)) +
 geom_col(show.legend = FALSE) +
 geom_text(aes(label = paste0(n, " (", Percentage, "%)")), hjust = -0.1, size = 5) +
 coord_flip() +
 scale_fill_manual(values = aptc_palette) +
 scale_y_continuous(limits = c(0, 50)) +
 labs(title = "Contract Length", x = NULL, y = "Percentage (%)") +
 theme_minimal(base_size = 16) +
 theme(plot.title = element_text(face = "bold", color = aptc_navy))
```

::: notes
Contract lengths vary considerably, with yearly contracts and tenured/permanent positions being most common.
:::

# Salary Analysis {background-color="#252b3b"}

## Overall Salary Distribution

```{r}
salary_stats <- dat %>%
 filter(!is.na(GrossSalary)) %>%
 summarise(N = n(), Mean = mean(GrossSalary), SD = sd(GrossSalary),
           Median = median(GrossSalary), Q1 = quantile(GrossSalary, 0.25),
           Q3 = quantile(GrossSalary, 0.75))

dat %>%
 filter(!is.na(GrossSalary)) %>%
 ggplot(aes(x = GrossSalary)) +
 geom_histogram(binwidth = 10000, fill = aptc_teal, color = "white", alpha = 0.9) +
 geom_vline(aes(xintercept = median(GrossSalary)), color = aptc_coral, 
            linetype = "dashed", linewidth = 1.2) +
 scale_x_continuous(labels = dollar_format()) +
 labs(title = "Gross Salary Distribution",
      subtitle = paste0("Median = ", dollar(salary_stats$Median), " | Mean = ", dollar(round(salary_stats$Mean))),
      x = "Gross Salary", y = "Count") +
 theme_minimal(base_size = 16) +
 theme(plot.title = element_text(face = "bold", color = aptc_navy))
```

::: notes
The median gross salary is approximately \$104,000, with a mean of \$106,000. There is considerable variation across positions.
:::

## Salary by Academic Rank

```{r}
dat %>%
 filter(!is.na(GrossSalary), !is.na(RankGrp)) %>%
 ggplot(aes(x = reorder(RankGrp, GrossSalary, median), y = GrossSalary, fill = RankGrp)) +
 geom_boxplot(alpha = 0.8, show.legend = FALSE) +
 geom_jitter(width = 0.2, alpha = 0.3, size = 2) +
 coord_flip() +
 scale_y_continuous(labels = dollar_format()) +
 scale_fill_manual(values = aptc_palette) +
 labs(title = "Gross Salary by Academic Rank", x = NULL, y = "Gross Salary") +
 theme_minimal(base_size = 16) +
 theme(plot.title = element_text(face = "bold", color = aptc_navy))
```

::: notes
As expected, salary increases with rank progression. Full professors have the highest median salary, followed by associate and assistant professors.
:::

## Salary Summary Table

```{r}
salary_by_rank <- dat %>%
 filter(!is.na(GrossSalary), !is.na(RankGrp)) %>%
 group_by(RankGrp) %>%
 summarise(N = n(), Mean = mean(GrossSalary), Median = median(GrossSalary),
           SD = sd(GrossSalary), .groups = "drop") %>%
 arrange(desc(Median))

salary_by_rank %>%
 mutate(Mean = dollar(round(Mean)), Median = dollar(round(Median)), 
        SD = dollar(round(SD))) %>%
 kable(col.names = c("Rank", "N", "Mean", "Median", "SD")) %>%
 kable_styling(bootstrap_options = c("striped", "hover"), font_size = 20)
```

::: notes
This table shows salary statistics by rank. Note that cells with fewer than 3 respondents are suppressed for privacy.
:::

## Salary by Contract Length

```{r}
dat %>%
 filter(!is.na(GrossSalary), !is.na(ContractLength)) %>%
 ggplot(aes(x = reorder(ContractLength, GrossSalary, median), y = GrossSalary, fill = ContractLength)) +
 geom_boxplot(alpha = 0.8, show.legend = FALSE) +
 geom_jitter(width = 0.2, alpha = 0.3, size = 2) +
 coord_flip() +
 scale_y_continuous(labels = dollar_format()) +
 scale_fill_manual(values = aptc_palette) +
 labs(title = "Salary by Contract Length", x = NULL, y = "Gross Salary") +
 theme_minimal(base_size = 16) +
 theme(plot.title = element_text(face = "bold", color = aptc_navy))
```

::: notes
Tenured and permanent positions tend to have higher salaries than yearly or multi-year contracts.
:::

# Clinic Operations {background-color="#252b3b"}

## Clinic Age & Training Model

::::: columns
::: {.column width="50%"}
```{r}
age_stats <- dat %>%
 filter(!is.na(ClinicAge), ClinicAge >= 0) %>%
 summarise(N = n(), Mean = mean(ClinicAge), Median = median(ClinicAge))

dat %>%
 filter(!is.na(ClinicAge), ClinicAge >= 0) %>%
 ggplot(aes(x = ClinicAge)) +
 geom_histogram(binwidth = 5, fill = aptc_teal, color = "white", alpha = 0.9) +
 geom_vline(aes(xintercept = median(ClinicAge)), color = aptc_coral, 
            linetype = "dashed", linewidth = 1.2) +
 labs(title = "Clinic Age (Years)",
      subtitle = paste0("Median = ", age_stats$Median, " years"),
      x = "Years", y = "Count") +
 theme_minimal(base_size = 14) +
 theme(plot.title = element_text(face = "bold", color = aptc_navy))
```
:::

::: {.column width="50%"}
```{r}
model_summary <- dat %>%
 filter(!is.na(ClinicTrainingModel)) %>%
 count(ClinicTrainingModel) %>%
 mutate(Percentage = round(100 * n / sum(n), 1)) %>%
 arrange(desc(n))

ggplot(model_summary, aes(x = reorder(ClinicTrainingModel, n), y = Percentage, fill = ClinicTrainingModel)) +
 geom_col(show.legend = FALSE) +
 geom_text(aes(label = paste0(n, "\n(", Percentage, "%)")), hjust = -0.1, size = 4) +
 coord_flip() +
 scale_fill_manual(values = aptc_palette) +
 scale_y_continuous(limits = c(0, 80)) +
 labs(title = "Training Model", x = NULL, y = "Percentage (%)") +
 theme_minimal(base_size = 14) +
 theme(plot.title = element_text(face = "bold", color = aptc_navy))
```
:::
:::::

::: notes
Most clinics have been operating for decades. The scientist-practitioner model remains the most common training approach.
:::

## Clinic Size: Clients & Trainees

::::: columns
::: {.column width="50%"}
```{r}
client_stats <- dat %>%
 filter(!is.na(ClinicClientsCount), ClinicClientsCount > 0) %>%
 summarise(N = n(), Mean = mean(ClinicClientsCount), Median = median(ClinicClientsCount))

dat %>%
 filter(!is.na(ClinicClientsCount), ClinicClientsCount > 0, ClinicClientsCount < 500) %>%
 ggplot(aes(x = ClinicClientsCount)) +
 geom_histogram(binwidth = 25, fill = aptc_coral, color = "white", alpha = 0.9) +
 geom_vline(aes(xintercept = median(ClinicClientsCount)), color = aptc_navy, 
            linetype = "dashed", linewidth = 1.2) +
 labs(title = "Clients per Year",
      subtitle = paste0("Median = ", round(client_stats$Median)),
      x = "Number of Clients", y = "Count") +
 theme_minimal(base_size = 14) +
 theme(plot.title = element_text(face = "bold", color = aptc_navy))
```
:::

::: {.column width="50%"}
```{r}
trainee_stats <- dat %>%
 filter(!is.na(ClinicTotalTrainees), ClinicTotalTrainees > 0) %>%
 summarise(N = n(), Mean = mean(ClinicTotalTrainees), Median = median(ClinicTotalTrainees))

dat %>%
 filter(!is.na(ClinicTotalTrainees), ClinicTotalTrainees > 0) %>%
 ggplot(aes(x = ClinicTotalTrainees)) +
 geom_histogram(binwidth = 5, fill = aptc_teal, color = "white", alpha = 0.9) +
 geom_vline(aes(xintercept = median(ClinicTotalTrainees)), color = aptc_coral, 
            linetype = "dashed", linewidth = 1.2) +
 labs(title = "Trainees per Year",
      subtitle = paste0("Median = ", round(trainee_stats$Median)),
      x = "Number of Trainees", y = "Count") +
 theme_minimal(base_size = 14) +
 theme(plot.title = element_text(face = "bold", color = aptc_navy))
```
:::
:::::

::: notes
Clinic sizes vary considerably. The median clinic serves around 110 clients and trains approximately 15 students per year.
:::

## Clinic Space

```{r}
sqft_summary <- dat %>%
 filter(!is.na(ClinSqFt)) %>%
 count(ClinSqFt) %>%
 mutate(Percentage = round(100 * n / sum(n), 1))

ggplot(sqft_summary, aes(x = ClinSqFt, y = n, fill = ClinSqFt)) +
 geom_col(show.legend = FALSE) +
 geom_text(aes(label = paste0(n, "\n(", Percentage, "%)")), vjust = -0.2, size = 5) +
 scale_fill_manual(values = aptc_palette) +
 scale_y_continuous(limits = c(0, max(sqft_summary$n) * 1.3)) +
 labs(title = "Clinic Space Distribution", 
      subtitle = paste0("N = ", sum(sqft_summary$n)),
      x = NULL, y = "Count") +
 theme_minimal(base_size = 16) +
 theme(plot.title = element_text(face = "bold", color = aptc_navy),
       axis.text.x = element_text(angle = 45, hjust = 1))
```

::: notes
Most clinics fall in the 1,000 to 5,000 square foot range, with the most common category being 2,000-4,999 square feet.
:::

## Staff Composition

```{r}
staff_presence <- dat %>%
 summarise(
   `Has Support Staff` = mean(ClinicSupportStaff == "Yes", na.rm = TRUE) * 100,
   `Has Grad Staff` = mean(GradStaff == "Yes", na.rm = TRUE) * 100,
   `Has Undergrad Staff` = mean(UgradStaff == "Yes", na.rm = TRUE) * 100,
   `Has Postdocs` = mean(PostDocsBinary == "Yes", na.rm = TRUE) * 100
 ) %>%
 pivot_longer(everything(), names_to = "Staff Type", values_to = "Percentage")

ggplot(staff_presence, aes(x = reorder(`Staff Type`, Percentage), y = Percentage, fill = `Staff Type`)) +
 geom_col(show.legend = FALSE) +
 geom_text(aes(label = paste0(round(Percentage, 0), "%")), hjust = -0.1, size = 5) +
 coord_flip() +
 scale_y_continuous(limits = c(0, 100)) +
 scale_fill_manual(values = aptc_palette) +
 labs(title = "Percentage of Clinics with Various Staff Types", x = NULL, y = "Percentage (%)") +
 theme_minimal(base_size = 16) +
 theme(plot.title = element_text(face = "bold", color = aptc_navy))
```

::: notes
Most clinics have support staff and graduate assistants. Fewer have undergraduate staff, and only about 9% have postdoctoral trainees.
:::

# Services & Fees {background-color="#252b3b"}

## Services Offered

:::::: columns
::: {.column width="50%"}
```{r}
therapy_pct <- sum(dat$ClinicTherapyBinary == "Yes", na.rm = TRUE) / 
              sum(!is.na(dat$ClinicTherapyBinary)) * 100
assess_pct <- sum(dat$ClinicAssmntBinary == "Yes", na.rm = TRUE) / 
             sum(!is.na(dat$ClinicAssmntBinary)) * 100

services <- tibble(
 Service = c("Therapy", "Assessment"),
 Percentage = c(therapy_pct, assess_pct)
)

ggplot(services, aes(x = Service, y = Percentage, fill = Service)) +
 geom_col(show.legend = FALSE) +
 geom_text(aes(label = paste0(round(Percentage, 0), "%")), vjust = -0.5, size = 6) +
 scale_y_continuous(limits = c(0, 110)) +
 scale_fill_manual(values = c(aptc_teal, aptc_coral)) +
 labs(title = "Services Offered", x = NULL, y = "Percentage (%)") +
 theme_minimal(base_size = 16) +
 theme(plot.title = element_text(face = "bold", color = aptc_navy))
```
:::

:::: {.column width="50%"}
### Service Highlights

-   **`r round(therapy_pct)`%** offer therapy
-   **`r round(assess_pct)`%** offer assessment
-   Most clinics offer both services

```{r}
sliding <- sum(dat$ClinicSlidingScale == "Yes", na.rm = TRUE) / 
          sum(!is.na(dat$ClinicSlidingScale)) * 100
```

::: callout-tip
**`r round(sliding)`%** of clinics use sliding scale fees
:::
::::
::::::

::: notes
Nearly all clinics offer therapy services, with assessment also being very common. The majority use sliding scale fee structures.
:::

## Clinic Revenue

```{r}
revenue_stats <- dat %>%
 filter(!is.na(ClinicRevenue), ClinicRevenue > 0) %>%
 summarise(N = n(), Mean = mean(ClinicRevenue), Median = median(ClinicRevenue),
           Min = min(ClinicRevenue), Max = max(ClinicRevenue))

dat %>%
 filter(!is.na(ClinicRevenue), ClinicRevenue > 0, ClinicRevenue < 500000) %>%
 ggplot(aes(x = ClinicRevenue)) +
 geom_histogram(binwidth = 25000, fill = aptc_teal, color = "white", alpha = 0.9) +
 geom_vline(aes(xintercept = median(ClinicRevenue)), color = aptc_coral, 
            linetype = "dashed", linewidth = 1.2) +
 scale_x_continuous(labels = dollar_format()) +
 labs(title = "Annual Clinic Revenue",
      subtitle = paste0("Median = ", dollar(revenue_stats$Median), " (N = ", revenue_stats$N, ")"),
      x = "Revenue", y = "Count") +
 theme_minimal(base_size = 16) +
 theme(plot.title = element_text(face = "bold", color = aptc_navy))
```

::: notes
Median clinic revenue is approximately \$44,000, though there is substantial variation. Some clinics generate over \$500,000 annually.
:::

# Technology {background-color="#252b3b"}

## EMR & Telehealth Adoption

::::: columns
::: {.column width="50%"}
```{r}
emr_summary <- dat %>%
 filter(!is.na(EMRbinary)) %>%
 count(EMRbinary) %>%
 mutate(Percentage = round(100 * n / sum(n), 1))

ggplot(emr_summary, aes(x = EMRbinary, y = Percentage, fill = EMRbinary)) +
 geom_col(show.legend = FALSE) +
 geom_text(aes(label = paste0(n, "\n(", Percentage, "%)")), vjust = -0.3, size = 5) +
 scale_y_continuous(limits = c(0, 100)) +
 scale_fill_manual(values = c("Yes" = aptc_teal, "No" = aptc_coral)) +
 labs(title = "EMR Usage", x = NULL, y = "Percentage (%)") +
 theme_minimal(base_size = 14) +
 theme(plot.title = element_text(face = "bold", color = aptc_navy))
```
:::

::: {.column width="50%"}
```{r}
telehealth_summary <- dat %>%
 filter(!is.na(Telehealth)) %>%
 count(Telehealth) %>%
 mutate(Percentage = round(100 * n / sum(n), 1))

ggplot(telehealth_summary, aes(x = Telehealth, y = Percentage, fill = Telehealth)) +
 geom_col(show.legend = FALSE) +
 geom_text(aes(label = paste0(n, "\n(", Percentage, "%)")), vjust = -0.3, size = 5) +
 scale_y_continuous(limits = c(0, 100)) +
 scale_fill_manual(values = aptc_palette) +
 labs(title = "Telehealth Services", x = NULL, y = "Percentage (%)") +
 theme_minimal(base_size = 14) +
 theme(plot.title = element_text(face = "bold", color = aptc_navy))
```
:::
:::::

::: notes
Most clinics have adopted electronic medical records and offer telehealth services, reflecting the ongoing digital transformation in healthcare training.
:::

# Director Wellbeing {background-color="#252b3b"}

## Burnout Indicators

```{r}
burnout_items <- c(
 "Burnout_1" = "Emotional exhaustion",
 "Burnout_2" = "Depersonalization", 
 "Burnout_3" = "Reduced accomplishment",
 "Burnout_4" = "Work-life conflict",
 "Burnout_5" = "Intent to leave"
)

burnout_summary <- dat %>%
 select(starts_with("Burnout_")) %>%
 pivot_longer(everything(), names_to = "Item", values_to = "Score") %>%
 filter(!is.na(Score)) %>%
 group_by(Item) %>%
 summarise(N = n(), Mean = mean(Score), SD = sd(Score), .groups = "drop") %>%
 mutate(Label = burnout_items[Item])

ggplot(burnout_summary, aes(x = reorder(Label, Mean), y = Mean, fill = Label)) +
 geom_col(show.legend = FALSE) +
 geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), width = 0.2, color = aptc_navy) +
 geom_text(aes(label = round(Mean, 1)), hjust = -0.3, size = 5) +
 coord_flip() +
 scale_fill_manual(values = aptc_palette) +
 scale_y_continuous(limits = c(0, 6)) +
 labs(title = "Burnout Indicators",
      subtitle = "Mean scores (error bars = ±1 SD)",
      x = NULL, y = "Mean Score") +
 theme_minimal(base_size = 16) +
 theme(plot.title = element_text(face = "bold", color = aptc_navy))
```

::: notes
Burnout scores vary across dimensions. These indicators help us understand the challenges clinic directors face and can inform support initiatives.
:::

# Summary {background-color="#252b3b"}

## Key Takeaways

::::: columns
::: {.column width="50%"}
### Sample & Position

-   **`r nrow(dat)`** respondents
-   Majority hold faculty positions
-   Median **`r role_stats$Median`** years in role

### Compensation

-   Median salary: **`r dollar(salary_stats$Median)`**
-   Clear progression by rank
-   Most receive PD funding
:::

::: {.column width="50%"}
### Clinic Operations

-   Median **`r round(client_stats$Median)`** clients/year
-   Most offer therapy + assessment
-   Strong tech adoption (EMR, telehealth)

### Staffing

-   **\~75%** have support staff
-   **\~67%** have grad assistants
-   **\~9%** have postdocs
:::
:::::

::: notes
In summary, APTC clinics continue to play a vital role in training the next generation of psychologists while serving diverse client populations. Directors face various challenges but demonstrate resilience and commitment to their roles.
:::

## Questions?

::::: columns
::: {.column width="60%"}
### Contact Us

**Jacqueline Hersh, Ph.D.** Research Committee Chair

**Ryan L. Farmer, Ph.D.** Research Committee Member
:::

::: {.column width="40%"}
### Resources

-   Full analysis report available
-   Data requests: Contact Research Committee
-   APTC Website: [aptc.org](https://aptc.org)
:::
:::::

::: notes
Thank you for your attention. We welcome questions about these findings and encourage members to reach out with data requests or suggestions for future surveys.
:::
