---
title: "Psychology Training Clinics: 2026 APTC Comprehensive Analysis"
author: "Jacqueline Hersh, Ph.D. & Ryan L. Farmer, Ph.D."
date: today
format:
  html:
    toc: true
    toc-depth: 3
    toc-float: true
    number-sections: true
    code-fold: true
    code-tools: true
    theme: cosmo
    df-print: paged
    fig-width: 10
    fig-height: 6
editor: visual
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  message = FALSE,
  fig.align = "center"
)

# -----------------------------
# APTC Color System
# -----------------------------

# Core brand colors
aptc_navy  <- "#252b3b"
aptc_coral <- "#ff6544"
aptc_teal  <- "#31a8c0"
aptc_white <- "#ffffff"

# Extended categorical palette (9 colors, stable + on-brand)
aptc_palette <- c(
  aptc_coral,
  "#ff8f77",
  "#e24f33",
  aptc_teal,
  "#5bc0d4",
  "#1f7f92",
  aptc_navy,
  "#454d5f",
  "#161b29"
)

# Binary palette (Yes / No, True / False, etc.)
aptc_binary <- c(aptc_teal, aptc_coral)

# Sequential palette (low -> high)
aptc_sequential <- colorRampPalette(c(aptc_white, aptc_teal, aptc_navy))(100)
```

# Setup and Data Loading

## Load Libraries

```{r libraries}
library(readxl)
library(tidyverse)
library(freqtables)
library(skimr)
library(scales)
library(gt)
library(knitr)
library(kableExtra)
library(patchwork)
library(viridis)
```

## Load Data

```{r load-data}
# Load raw data
dat <- read_excel("dat.xlsx")
dat <- dat[-1, ]

# -----------------------------
# GLOBAL DATA CLEANING
# -----------------------------

dat <- dat %>%
  mutate(across(where(is.numeric), ~ na_if(., -99))) %>%
  mutate(across(where(is.character), ~ na_if(., "-99"))) %>%
  mutate(
    across(
      where(is.character),
      ~ if_else(
        str_detect(., regex("(\\?$)|(^what is )|(^last )|(^during )|(^in the last )", ignore_case = TRUE)),
        NA_character_, .
      )
    )
  ) %>%
  mutate(across(where(is.character), str_trim)) %>%
  mutate(
    across(
      matches("Binary$"),
      ~ case_when(
        str_detect(., regex("^yes$", ignore_case = TRUE)) ~ "Yes",
        str_detect(., regex("^no$",  ignore_case = TRUE)) ~ "No",
        TRUE ~ NA_character_
      )
    )
  ) %>%
  mutate(
    Progress = as.numeric(Progress),
    Duration = as.numeric(`Duration (in seconds)`),
    GrossSalary = as.numeric(GrossSalary),
    FTESalary = as.numeric(FTESalary),
    RoleDuration = as.numeric(RoleDuration),
    ClinicDuration = as.numeric(ClinicDuration),
    ClinicAge = as.numeric(ClinicAge),
    HoursWorkClinic = as.numeric(HoursWorkClinic),
    CoursesTaught = as.numeric(CoursesTaught),
    CourseCreditHours = as.numeric(CourseCreditHours),
    ClinicTotalTrainees = as.numeric(ClinicTotalTrainees),
    ClinicClientsCount = as.numeric(ClinicClientsCount),
    NumRooms = as.numeric(NumRooms),
    ClinSqFt = as.numeric(ClinSqFt),
    SupTraineeCount = as.numeric(SupTraineeCount),
    MaxTraineeCount = as.numeric(MaxTraineeCount),
    HoursSupTherapy = as.numeric(HoursSupTherapy),
    HoursSupAssmnt = as.numeric(HoursSupAssmnt),
    HoursSupSup = as.numeric(HoursSupSup),
    HoursWatching = as.numeric(HoursWatching),
    HoursReviewingDoc = as.numeric(HoursReviewingDoc),
    MaxTraineesTherapy = as.numeric(MaxTraineesTherapy),
    MaxTraineesAssmnt = as.numeric(MaxTraineesAssmnt),
    TxLength = as.numeric(TxLength),
    MaxTxCasesAllow = as.numeric(MaxTxCasesAllow),
    MaxAxCasesAllow = as.numeric(MaxAxCasesAllow),
    ClinicRevenue = as.numeric(ClinicRevenue),
    ClinicTxRevenue = as.numeric(ClinicTxRevenue),
    ClinicAxRevenue = as.numeric(ClinicAxRevenue),
    Burnout_1 = as.numeric(Burnout_1),
    Burnout_2 = as.numeric(Burnout_2),
    Burnout_3 = as.numeric(Burnout_3),
    Burnout_4 = as.numeric(Burnout_4),
    Burnout_5 = as.numeric(Burnout_5)
  )

cat("Total respondents:", nrow(dat), "\n")
cat("Number of variables:", ncol(dat), "\n")
```

## Helper Functions

```{r helpers}
# Function to handle NA as empty string
nz <- function(x) ifelse(is.na(x), "", x)

# -----------------------------
# IMPROVED TENURE TRACK CLASSIFICATION
# -----------------------------

is_tt <- function(x) {
  s <- nz(x)
  str_detect(s, regex("^Tenured or Tenure-track", ignore_case = TRUE)) |
    (str_detect(s, regex("\\b(tenured|tenure[- ]?track)\\b", ignore_case = TRUE)) &
       !str_detect(s, regex("\\bnon[- ]?tenure", ignore_case = TRUE)))
}

is_ntt <- function(x) {
  s <- nz(x)
  str_detect(s, regex("\\bnon[- ]?tenure", ignore_case = TRUE)) |
    str_detect(s, regex("\\b(adjunct|lecturer|teaching faculty|clinical faculty)\\b", ignore_case = TRUE))
}

# Prepare salary data with rank groups
dat_simple <- dat %>%
  mutate(
    GrossSalary = parse_number(as.character(GrossSalary)),
    GrossSalary = ifelse(is.na(GrossSalary) | GrossSalary <= 0, NA_real_, GrossSalary),
    FullPart = case_when(
      str_detect(nz(FullPart), regex("part", ignore_case = TRUE)) ~ "Part-time",
      str_detect(nz(FullPart), regex("full", ignore_case = TRUE)) ~ "Full-time",
      TRUE ~ NA_character_
    ),
    RankGrp = case_when(
      str_detect(nz(Rank), regex("^Assistant", ignore_case = TRUE)) ~ "Assistant Professor",
      str_detect(nz(Rank), regex("^Associate", ignore_case = TRUE)) ~ "Associate Professor",
      str_detect(nz(Rank), regex("^Full", ignore_case = TRUE)) ~ "Full Professor",
      str_detect(nz(RoleTitle), regex("lecturer", ignore_case = TRUE)) |
        str_detect(nz(PositionType), regex("lecturer", ignore_case = TRUE)) ~ "Lecturer",
      str_detect(nz(RoleTitle), regex("staff", ignore_case = TRUE)) ~ "Staff (N/A)",
      !is.na(Rank) ~ "Other (specified)",
      TRUE ~ "Unspecified Rank"
    ),
    RankGrp = factor(RankGrp, levels = c("Assistant Professor", "Associate Professor", "Full Professor",
                                          "Lecturer", "Staff (N/A)", "Other (specified)", "Unspecified Rank"))
  )
```

## Data Quality Checks

```{r data-quality-checks}
sample_summary <- data.frame(
  Metric = c("Total Responses", "Finished Responses", "Progress = 100%", "Final Analytic Sample"),
  Count = c(nrow(read_excel("dat.xlsx")), sum(dat$Finished == "True", na.rm = TRUE),
            sum(dat$Progress == 100, na.rm = TRUE), nrow(dat))
)

sample_summary %>%
  kable(caption = "Sample Size Verification") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

cat("\n=== Membership Status ===\n")
print(table(dat$MemStatus, useNA = "always"))

cat("\n=== Professional Degree ===\n")
print(table(dat$ProfDeg, useNA = "always"))

cat("\n=== Position Type (first 5 unique values) ===\n")
print(head(sort(table(dat$PositionType, useNA = "always"), decreasing = TRUE), 5))
```

### Missing Data Analysis

```{r missing-data-analysis}
key_vars <- c("GrossSalary", "FTESalary", "RoleDuration", "ClinicDuration", "Rank", "PositionType",
              "FullPart", "ContractLength", "TeachingBinary", "CoursesTaught", "ClinicAge",
              "ClinicTrainingModel", "ClinicTotalTrainees", "ClinicClientsCount", "ClinicRevenue",
              "ClinicSlidingScale", "EMRbinary", "Telehealth", "ResearchActive", "Burnout_1", "MaxTraineeCount")

missing_summary <- dat %>%
  select(any_of(key_vars)) %>%
  summarise(across(everything(), ~sum(is.na(.)))) %>%
  pivot_longer(everything(), names_to = "Variable", values_to = "Missing_Count") %>%
  mutate(Total = nrow(dat), Percent_Missing = round(100 * Missing_Count / Total, 1),
         Percent_Complete = 100 - Percent_Missing) %>%
  arrange(desc(Percent_Missing))

missing_summary %>%
  filter(Missing_Count > 0) %>%
  kable(caption = "Missing Data Summary (Variables with Any Missing Data)") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

high_missing <- missing_summary %>% filter(Percent_Missing > 20)
if (nrow(high_missing) > 0) {
  cat("\n⚠️ WARNING: The following variables have >20% missing data:\n")
  print(high_missing %>% select(Variable, Percent_Missing))
}
```

### Numeric Data Range Checks

```{r numeric-range-checks}
salary_checks <- dat %>%
  filter(!is.na(GrossSalary)) %>%
  summarise(N = n(), Min = min(GrossSalary), Q1 = quantile(GrossSalary, 0.25),
            Median = median(GrossSalary), Mean = mean(GrossSalary), Q3 = quantile(GrossSalary, 0.75),
            Max = max(GrossSalary), N_Below_30K = sum(GrossSalary < 30000), N_Above_200K = sum(GrossSalary > 200000))

salary_checks %>%
  mutate(across(c(Min, Q1, Median, Mean, Q3, Max), ~dollar(.))) %>%
  kable(caption = "Salary Data Quality Check") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

if (salary_checks$N_Below_30K > 0) cat("\n⚠️ NOTE:", salary_checks$N_Below_30K, "salaries below $30,000.\n")
if (salary_checks$N_Above_200K > 0) cat("\n⚠️ NOTE:", salary_checks$N_Above_200K, "salaries above $200,000.\n")

revenue_checks <- dat %>%
  filter(!is.na(ClinicRevenue), ClinicRevenue > 0) %>%
  summarise(N = n(), Min = min(ClinicRevenue), Q1 = quantile(ClinicRevenue, 0.25),
            Median = median(ClinicRevenue), Mean = mean(ClinicRevenue), Q3 = quantile(ClinicRevenue, 0.75),
            Max = max(ClinicRevenue), N_Above_500K = sum(ClinicRevenue > 500000), N_Above_1M = sum(ClinicRevenue > 1000000))

revenue_checks %>%
  mutate(across(c(Min, Q1, Median, Mean, Q3, Max), ~dollar(.))) %>%
  kable(caption = "Revenue Data Quality Check") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```

### Tenure Track Classification Verification

```{r tenure-classification-check}
tenure_check <- dat %>%
  filter(!is.na(PositionType)) %>%
  mutate(TT = is_tt(PositionType), NTT = is_ntt(PositionType),
         Classification = case_when(TT & NTT ~ "CONFLICT", TT ~ "Tenure-Track/Tenured",
                                    NTT ~ "Non-Tenure-Track", TRUE ~ "Unclassified")) %>%
  count(Classification, PositionType) %>%
  arrange(Classification, desc(n))

tenure_check %>%
  kable(caption = "Tenure Track Classification Check") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

unclassified <- tenure_check %>% filter(Classification == "Unclassified")
if (nrow(unclassified) > 0) {
  cat("\n⚠️ NOTE:", sum(unclassified$n), "positions could not be classified as TT or NTT.\n")
}
```

### Sample Sizes for Salary Tables

```{r salary-table-cell-sizes}
cell_sizes <- dat_simple %>%
  filter(!is.na(GrossSalary), !is.na(RankGrp), !is.na(FullPart)) %>%
  count(RankGrp, FullPart) %>%
  pivot_wider(names_from = FullPart, values_from = n, values_fill = 0) %>%
  mutate(`Full-time` = ifelse(`Full-time` < 3, paste0(`Full-time`, " ⚠️"), as.character(`Full-time`)),
         `Part-time` = ifelse(`Part-time` < 3, paste0(`Part-time`, " ⚠️"), as.character(`Part-time`)))

cell_sizes %>%
  kable(caption = "Cell Sizes for Salary Tables (⚠️ = suppressed due to n<3)") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

cat("\nCells marked with ⚠️ will show as '—' in salary tables due to privacy protection (n < 3).\n")
```

# Sample Demographics

## Membership Status

```{r membership}
mem_status <- dat %>%
  count(MemStatus) %>%
  mutate(Percentage = round(100 * n / sum(n), 1), Label = paste0(n, " (", Percentage, "%)"))

mem_status %>%
  kable(caption = "Sample Membership Status") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```

## Professional Degree

```{r degree}
deg_summary <- dat %>%
  count(ProfDeg) %>%
  mutate(Percentage = round(100 * n / sum(n), 1)) %>%
  arrange(desc(n))

ggplot(deg_summary, aes(x = reorder(ProfDeg, n), y = Percentage, fill = ProfDeg)) +
  geom_col(show.legend = FALSE) +
  geom_text(aes(label = paste0(n, " (", Percentage, "%)")), hjust = -0.2, size = 4) +
  coord_flip() +
  scale_y_continuous(limits = c(0, 100), breaks = seq(0, 100, 20)) +
  scale_fill_manual(values = aptc_palette) +
  labs(title = "Professional Degrees", x = NULL, y = "Percentage (%)") +
  theme_minimal(base_size = 13) +
  theme(plot.title = element_text(face = "bold", color = aptc_navy), panel.grid.minor = element_blank())
```

## Degree Area

```{r degree-area}
deg_area <- dat %>%
  count(DegArea) %>%
  mutate(Percentage = round(100 * n / sum(n), 1)) %>%
  arrange(desc(n))

ggplot(deg_area, aes(x = reorder(DegArea, n), y = Percentage, fill = DegArea)) +
  geom_col(show.legend = FALSE) +
  geom_text(aes(label = paste0(n, " (", Percentage, "%)")), hjust = -0.2, size = 4) +
  coord_flip() +
  scale_y_continuous(limits = c(0, 100), breaks = seq(0, 100, 20)) +
  scale_fill_manual(values = aptc_palette) +
  labs(title = "Graduate Degree Areas", x = NULL, y = "Percentage (%)") +
  theme_minimal(base_size = 13) +
  theme(plot.title = element_text(face = "bold", color = aptc_navy), panel.grid.minor = element_blank())
```

## Role Duration

```{r role-duration}
role_stats <- dat %>%
  filter(!is.na(RoleDuration), RoleDuration >= 0) %>%
  summarise(N = n(), Mean = mean(RoleDuration), SD = sd(RoleDuration), Median = median(RoleDuration),
            Min = min(RoleDuration), Max = max(RoleDuration))

dat %>%
  filter(!is.na(RoleDuration), RoleDuration >= 0) %>%
  ggplot(aes(x = RoleDuration)) +
  geom_histogram(binwidth = 2, fill = aptc_teal, color = "white", alpha = 0.9) +
  geom_vline(aes(xintercept = median(RoleDuration)), color = aptc_coral, linetype = "dashed", linewidth = 1) +
  labs(title = "How Long Have Directors Been in Their Role?",
       subtitle = paste0("Mean = ", round(role_stats$Mean, 2), " years | Median = ", role_stats$Median, " years"),
       x = "Years in Role", y = "Count") +
  theme_minimal(base_size = 13) +
  theme(plot.title = element_text(face = "bold", color = aptc_navy))

role_stats %>% kable(digits = 2) %>% kable_styling()
```

# Position Characteristics

## Academic Rank by Tenure Status

```{r rank-tenure}
rank_tenure <- dat %>%
  filter(!is.na(Rank), !is.na(PositionType)) %>%
  mutate(
    Rank_clean = case_when(
      str_detect(Rank, regex("Assistant", ignore_case = TRUE)) ~ "Assistant Professor",
      str_detect(Rank, regex("Associate", ignore_case = TRUE)) ~ "Associate Professor",
      str_detect(Rank, regex("Full", ignore_case = TRUE)) ~ "Full Professor",
      TRUE ~ "Other"
    ),
    TenureStatus = case_when(is_tt(PositionType) ~ "TT/Tenured", is_ntt(PositionType) ~ "NTT", TRUE ~ "Other")
  ) %>%
  count(Rank_clean, TenureStatus) %>%
  pivot_wider(names_from = TenureStatus, values_from = n, values_fill = 0)

rank_tenure %>%
  kable(caption = "Academic Rank by Tenure Status") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```

## Supervisor

```{r supervisor}
sup_summary <- dat %>%
  count(Supervisor) %>%
  mutate(Percentage = round(100 * n / sum(n), 1)) %>%
  arrange(desc(n))

ggplot(sup_summary, aes(x = reorder(Supervisor, n), y = Percentage, fill = Supervisor)) +
  geom_col(show.legend = FALSE) +
  geom_text(aes(label = paste0(n, " (", Percentage, "%)")), hjust = -0.2, size = 3.5) +
  coord_flip() +
  scale_y_continuous(limits = c(0, 100), breaks = seq(0, 100, 20)) +
  scale_fill_manual(values = aptc_palette) +
  labs(title = "To Whom Do Clinic Directors Report?", x = NULL, y = "Percentage (%)") +
  theme_minimal(base_size = 13) +
  theme(plot.title = element_text(face = "bold", color = aptc_navy), panel.grid.minor = element_blank())
```

## Contract Characteristics

```{r contracts}
contract_months <- dat %>% count(ContractMonths) %>% mutate(Percentage = round(100 * n / sum(n), 1)) %>% arrange(desc(n))
contract_length <- dat %>% count(ContractLength) %>% mutate(Percentage = round(100 * n / sum(n), 1)) %>% arrange(desc(n))

p1 <- ggplot(contract_months, aes(x = reorder(ContractMonths, n), y = Percentage, fill = ContractMonths)) +
  geom_col(show.legend = FALSE) +
  geom_text(aes(label = paste0(n, " (", Percentage, "%)")), hjust = -0.2, size = 3) +
  coord_flip() + scale_y_continuous(limits = c(0, 100)) + scale_fill_manual(values = aptc_palette) +
  labs(title = "Contract Type (Months)", x = NULL, y = "Percentage (%)") +
  theme_minimal(base_size = 11) + theme(plot.title = element_text(face = "bold", color = aptc_navy))

p2 <- ggplot(contract_length, aes(x = reorder(ContractLength, n), y = Percentage, fill = ContractLength)) +
  geom_col(show.legend = FALSE) +
  geom_text(aes(label = paste0(n, " (", Percentage, "%)")), hjust = -0.2, size = 3) +
  coord_flip() + scale_y_continuous(limits = c(0, 100)) + scale_fill_manual(values = aptc_palette) +
  labs(title = "Contract Length", x = NULL, y = "Percentage (%)") +
  theme_minimal(base_size = 11) + theme(plot.title = element_text(face = "bold", color = aptc_navy))

p1 + p2
```

# Salary Analysis

## Overall Salary Distribution

```{r salary-overall}
salary_stats <- dat_simple %>%
  filter(!is.na(GrossSalary)) %>%
  summarise(N = n(), Mean = mean(GrossSalary), SD = sd(GrossSalary), Median = median(GrossSalary),
            Q1 = quantile(GrossSalary, 0.25), Q3 = quantile(GrossSalary, 0.75),
            Min = min(GrossSalary), Max = max(GrossSalary))

dat_simple %>%
  filter(!is.na(GrossSalary)) %>%
  ggplot(aes(x = GrossSalary)) +
  geom_histogram(binwidth = 10000, fill = aptc_teal, color = "white", alpha = 0.9) +
  geom_vline(aes(xintercept = median(GrossSalary)), color = aptc_coral, linetype = "dashed", linewidth = 1) +
  scale_x_continuous(labels = dollar_format()) +
  labs(title = "Gross Salary Distribution",
       subtitle = paste0("Median = ", dollar(salary_stats$Median), " | Mean = ", dollar(salary_stats$Mean)),
       x = "Gross Salary", y = "Count") +
  theme_minimal(base_size = 13) +
  theme(plot.title = element_text(face = "bold", color = aptc_navy))

# FIX: Format only dollar columns, not N
salary_stats %>%
  mutate(across(c(Mean, SD, Median, Q1, Q3, Min, Max), ~dollar(.))) %>%
  kable(caption = "Overall Salary Statistics") %>%
  kable_styling()
```

## Salary by Rank and Full-Time/Part-Time

```{r salary-tables}
make_salary_table <- function(df) {
  df %>%
    filter(!is.na(GrossSalary), FullPart %in% c("Full-time", "Part-time")) %>%
    group_by(RankGrp, FullPart) %>%
    summarise(n = n(), avg = mean(GrossSalary), .groups = "drop") %>%
    mutate(val = ifelse(n >= 3, dollar(round(avg, 0)), "—")) %>%
    select(RankGrp, FullPart, val) %>%
    complete(RankGrp, FullPart = c("Full-time", "Part-time")) %>%
    pivot_wider(names_from = FullPart, values_from = val, names_glue = "Avg. {FullPart} Salary") %>%
    group_by(RankGrp) %>%
    summarise(`Avg. Full-time Salary` = first(na.omit(`Avg. Full-time Salary`)),
              `Avg. Part-time Salary` = first(na.omit(`Avg. Part-time Salary`)), .groups = "drop") %>%
    mutate(`Avg. Full-Time Salary` = ifelse(is.na(`Avg. Full-time Salary`), "—", `Avg. Full-time Salary`),
           `Avg. Part-Time Salary*` = ifelse(is.na(`Avg. Part-time Salary`), "—", `Avg. Part-time Salary`)) %>%
    select(`Rank / Role` = RankGrp, `Avg. Full-Time Salary`, `Avg. Part-Time Salary*`) %>%
    arrange(`Rank / Role`)
}

overall_table <- make_salary_table(dat_simple)

overall_table %>%
  gt() %>%
  tab_header(title = md("**Average Faculty Salaries — All Positions**"),
             subtitle = "Full-time and Part-time Averages (suppressed if n < 3)") %>%
  tab_style(style = cell_text(weight = "bold"), locations = cells_column_labels(everything())) %>%
  tab_source_note(source_note = md("*Cells suppressed when based on fewer than 3 respondents*"))
```

```{r salary-by-gender}
salary_gender_stats <- dat_simple %>%
  filter(!is.na(GrossSalary), !is.na(Gender)) %>%
  group_by(Gender) %>%
  summarise(N = n(), Mean = mean(GrossSalary), SD = sd(GrossSalary), Median = median(GrossSalary),
            Q1 = quantile(GrossSalary, 0.25), Q3 = quantile(GrossSalary, 0.75),
            Min = min(GrossSalary), Max = max(GrossSalary), .groups = "drop")

# FIX: Format only dollar columns, not N
salary_gender_stats %>%
  mutate(across(c(Mean, SD, Median, Q1, Q3, Min, Max), ~dollar(.))) %>%
  kable(caption = "Salary by Gender") %>%
  kable_styling()
```

### Tenure-Track/Tenured Positions

```{r salary-tt}
tt_table <- dat_simple %>% filter(is_tt(PositionType)) %>% make_salary_table()

tt_table %>%
  gt() %>%
  tab_header(title = md("**Average Faculty Salaries — Tenure/Tenure-Track (TT)**"),
             subtitle = "Full-time and Part-time Averages (suppressed if n < 3)") %>%
  tab_style(style = cell_text(weight = "bold"), locations = cells_column_labels(everything())) %>%
  tab_source_note(source_note = md("*Cells suppressed when based on fewer than 3 respondents*"))
```

### Non-Tenure-Track Positions

```{r salary-ntt}
ntt_table <- dat_simple %>% filter(is_ntt(PositionType)) %>% make_salary_table()

ntt_table %>%
  gt() %>%
  tab_header(title = md("**Average Faculty Salaries — Non-Tenure-Track (NTT)**"),
             subtitle = "Full-time and Part-time Averages (suppressed if n < 3)") %>%
  tab_style(style = cell_text(weight = "bold"), locations = cells_column_labels(everything())) %>%
  tab_source_note(source_note = md("*Cells suppressed when based on fewer than 3 respondents*"))
```

## Salary by Contract Type

```{r salary-contract}
dat_simple %>%
  filter(!is.na(GrossSalary), !is.na(ContractLength)) %>%
  ggplot(aes(x = reorder(ContractLength, GrossSalary, median), y = GrossSalary, fill = ContractLength)) +
  geom_boxplot(alpha = 0.8, show.legend = FALSE) +
  coord_flip() +
  scale_y_continuous(labels = dollar_format()) +
  scale_fill_manual(values = aptc_palette) +
  labs(title = "Salary by Contract Length", x = "Contract Length", y = "Gross Salary") +
  theme_minimal(base_size = 13) +
  theme(plot.title = element_text(face = "bold", color = aptc_navy))
```

**Note on Salary Tables:** The salary tables above show "—" (blank) cells when there are **fewer than 3 respondents** in that category. This is a privacy protection measure to prevent identification of individuals.

```{r salary-models}
salary_model_dat <- dat_simple %>%
  filter(!is.na(GrossSalary), !is.na(Gender), !is.na(RankGrp), !is.na(PositionType), !is.na(ContractLength)) %>%
  mutate(Gender_model = case_when(Gender %in% c("Man", "Woman") ~ Gender, TRUE ~ NA_character_),
         Gender_model = factor(Gender_model), RankGrp = factor(RankGrp),
         PositionType = factor(PositionType), ContractLength = factor(ContractLength)) %>%
  filter(!is.na(Gender_model))

salary_model <- lm(GrossSalary ~ Gender_model + RankGrp + PositionType + ContractLength, data = salary_model_dat)
summary(salary_model)

m_tt_ntt_rank <- lm(GrossSalary ~ PositionType + RankGrp + FullPart,
  data = dat_simple %>%
    filter(!is.na(GrossSalary),
           PositionType %in% c("Tenured or Tenure-track faculty",
                               "Non-tenure-track faculty (incl. Adjunct and teaching faculty)"),
           RankGrp %in% c("Assistant Professor", "Associate Professor", "Full Professor"),
           FullPart %in% c("Full-time", "Part-time")) %>%
    mutate(PositionType = relevel(factor(PositionType), ref = "Tenured or Tenure-track faculty"),
           RankGrp = factor(RankGrp, levels = c("Assistant Professor", "Associate Professor", "Full Professor")),
           FullPart = factor(FullPart)))
summary(m_tt_ntt_rank)
```

In an adjusted model accounting for rank, tenure status, and contract length, the estimated salary difference between men and women was \$10,832 (SE = \$9,000), which was not statistically significant (p = .23).

In a linear model restricted to faculty within the professorial rank structure and adjusting for full-time versus part-time status, tenure-track status was not independently associated with salary. Non-tenure-track faculty earned approximately \$13,000 less than tenure-track faculty on average, but this difference was not statistically significant (p = .17).

## Professional Development Funding

```{r pd-funding}
dat_simple <- dat_simple %>%
  mutate(PD_access = case_when(grepl("^Yes", PDFunds) ~ 1L, PDFunds == "No" ~ 0L, TRUE ~ NA_integer_),
         PD_amount = suppressWarnings(as.numeric(PDFunds_2_TEXT)),
         PD_amount = ifelse(PD_amount == -99, NA, PD_amount))

pd_summary <- dat %>% count(PDFunds) %>% mutate(Percentage = round(100 * n / sum(n), 1)) %>% arrange(desc(n))
pd_summary %>% kable(caption = "Professional Development Funding") %>% kable_styling(bootstrap_options = c("striped", "hover"))

pd_amount_dat <- dat_simple %>% filter(PD_access == 1, !is.na(PD_amount))

pd_amount_stats <- pd_amount_dat %>%
  summarise(N = n(), Mean = mean(PD_amount), SD = sd(PD_amount), Median = median(PD_amount),
            Q1 = quantile(PD_amount, 0.25), Q3 = quantile(PD_amount, 0.75),
            Min = min(PD_amount), Max = max(PD_amount))

# FIX: Format only dollar columns, not N
pd_amount_stats %>%
  mutate(across(c(Mean, SD, Median, Q1, Q3, Min, Max), ~dollar(.))) %>%
  kable(caption = "Professional Development Funding Amounts (Among Recipients)") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

ggplot(pd_amount_dat, aes(x = PD_amount)) +
  geom_histogram(binwidth = 500, fill = aptc_teal, color = "white", alpha = 0.9) +
  geom_vline(xintercept = median(pd_amount_dat$PD_amount, na.rm = TRUE), color = aptc_coral, linetype = "dashed", linewidth = 1) +
  scale_x_continuous(labels = dollar_format()) +
  labs(title = "Distribution of Professional Development Funding Amounts", x = "PD Funding (USD)", y = "Count") +
  theme_minimal(base_size = 13) +
  theme(plot.title = element_text(face = "bold", color = aptc_navy))
```

Among respondents who reported receiving professional development funds, dollar amounts did not differ significantly by tenure-track status, academic rank, or full-time appointment. PD funding amounts were relatively consistent across roles, with a typical allocation of approximately \$1,500–\$2,000 per year.

## Salary Funding Sources

```{r salary-funding-sources}
funding_vars <- c("FundingSrc_1" = "Department/University", "FundingSrc_2" = "College", "FundingSrc_3" = "Clinic Fees",
                  "FundingSrc_4" = "Individual Client Fees", "FundingSrc_5" = "Grants",
                  "FundingSrc_6" = "Community Contracts", "FundingSrc_7" = "Other")

funding_summary <- dat %>%
  select(starts_with("FundingSrc_")) %>% select(-contains("TEXT")) %>%
  summarise(across(everything(), ~sum(!is.na(.) & . != "0" & . != "", na.rm = TRUE))) %>%
  pivot_longer(everything(), names_to = "Variable", values_to = "Count") %>%
  mutate(Source = funding_vars[Variable], Percentage = round(100 * Count / nrow(dat), 1)) %>%
  filter(!is.na(Source)) %>% arrange(desc(Count))

ggplot(funding_summary, aes(x = reorder(Source, Count), y = Count, fill = Source)) +
  geom_col(show.legend = FALSE) +
  geom_text(aes(label = paste0(Count, " (", Percentage, "%)")), hjust = -0.1, size = 3.5) +
  coord_flip() + scale_fill_manual(values = aptc_palette) +
  labs(title = "Salary Funding Sources", subtitle = "Respondents could select multiple sources", x = NULL, y = "Number Endorsing") +
  theme_minimal(base_size = 13) +
  theme(plot.title = element_text(face = "bold", color = aptc_navy), panel.grid.minor = element_blank())
```

# Responsibilities and Workload

## Hours Worked in Clinic

```{r hours-clinic}
hours_stats <- dat %>%
  filter(!is.na(HoursWorkClinic)) %>%
  summarise(N = n(), Mean = mean(HoursWorkClinic), SD = sd(HoursWorkClinic),
            Median = median(HoursWorkClinic), Min = min(HoursWorkClinic), Max = max(HoursWorkClinic))

dat %>%
  filter(!is.na(HoursWorkClinic)) %>%
  ggplot(aes(x = HoursWorkClinic)) +
  geom_histogram(binwidth = 5, fill = aptc_teal, color = "white", alpha = 0.9) +
  geom_vline(aes(xintercept = median(HoursWorkClinic)), color = aptc_coral, linetype = "dashed", linewidth = 1) +
  labs(title = "Hours Per Week Spent on Clinic Activities",
       subtitle = paste0("Median = ", hours_stats$Median, " hours | Mean = ", round(hours_stats$Mean, 1), " hours"),
       x = "Hours per Week", y = "Count") +
  theme_minimal(base_size = 13) +
  theme(plot.title = element_text(face = "bold", color = aptc_navy))
```

## Responsibilities

```{r responsibilities}
resp_vars <- c("Responsibilities_1" = "Administration", "Responsibilities_2" = "Teaching",
               "Responsibilities_3" = "Supervision", "Responsibilities_4" = "Direct Patient Services",
               "Responsibilities_5" = "Research", "Responsibilities_6" = "University/Department Service",
               "Responsibilities_7" = "Community/Professional Service", "Responsibilities_8" = "External Practicum Placements",
               "Responsibilities_10" = "Official Mentoring", "Responsibilities_11" = "Unofficial Mentoring",
               "Responsibilities_13" = "Crisis Response", "Responsibilities_14" = "Consulting",
               "Responsibilities_15" = "Outreach", "Responsibilities_12" = "Other")

resp_summary <- dat %>%
  select(starts_with("Responsibilities_")) %>% select(-contains("TEXT")) %>%
  summarise(across(everything(), ~sum(!is.na(.) & . != "0" & . != "", na.rm = TRUE))) %>%
  pivot_longer(everything(), names_to = "Variable", values_to = "Count") %>%
  mutate(Responsibility = resp_vars[Variable], Percentage = round(100 * Count / nrow(dat), 1)) %>%
  filter(!is.na(Responsibility)) %>% arrange(desc(Count))

ggplot(resp_summary, aes(x = reorder(Responsibility, Count), y = Count, fill = Responsibility)) +
  geom_col(show.legend = FALSE) +
  geom_text(aes(label = paste0(Count, " (", Percentage, "%)")), hjust = -0.1, size = 3) +
  coord_flip() + scale_fill_manual(values = rep(aptc_palette, 2)) +
  labs(title = "Clinic Director Responsibilities", subtitle = "Respondents could select multiple responsibilities",
       x = NULL, y = "Number Endorsing") +
  theme_minimal(base_size = 12) +
  theme(plot.title = element_text(face = "bold", color = aptc_navy), panel.grid.minor = element_blank())
```

## Hours Spent on Clinic Activities

```{r hours-by-activity}
hours_vars <- tibble(Variable = c("HoursSupTherapy", "HoursSupAssmnt", "HoursSupSup", "HoursWatching", "HoursReviewingDoc"),
                     Activity = c("Supervising Therapy", "Supervising Assessment", "Vertical Supervision",
                                  "Reviewing Sessions", "Reviewing Documentation"))

hours_summary <- dat %>%
  select(all_of(hours_vars$Variable)) %>%
  pivot_longer(everything(), names_to = "Variable", values_to = "Hours") %>%
  filter(!is.na(Hours), Hours >= 0) %>%
  left_join(hours_vars, by = "Variable") %>%
  group_by(Activity) %>%
  summarise(N = n(), Mean = mean(Hours), SD = sd(Hours), Median = median(Hours),
            Min = min(Hours), Max = max(Hours), .groups = "drop") %>%
  arrange(desc(Mean))

hours_summary %>%
  mutate(across(where(is.numeric) & !matches("^N$"), ~round(., 1))) %>%
  kable(caption = "Hours Spent on Various Clinic Activities (per week)") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

ggplot(hours_summary, aes(x = reorder(Activity, Mean), y = Mean, fill = Activity)) +
  geom_col(show.legend = FALSE) +
  geom_errorbar(aes(ymin = pmax(0, Mean - SD), ymax = Mean + SD), width = 0.2, color = aptc_navy) +
  geom_text(aes(label = paste0(round(Mean, 1), " hrs")), hjust = -0.1, size = 3.5) +
  coord_flip() + scale_fill_manual(values = aptc_palette) +
  labs(title = "Hours Spent on Clinic Activities", subtitle = "Mean hours per week (error bars = ±1 SD)",
       x = NULL, y = "Hours per Week") +
  theme_minimal(base_size = 13) +
  theme(plot.title = element_text(face = "bold", color = aptc_navy), panel.grid.minor = element_blank())
```

## Teaching

```{r teaching}
teaching_summary <- dat %>% count(TeachingBinary) %>% mutate(Percentage = round(100 * n / sum(n), 1))

courses_summary <- dat %>%
  filter(TeachingBinary == "Yes", !is.na(CoursesTaught)) %>%
  summarise(N = n(), Mean = mean(CoursesTaught), Median = median(CoursesTaught),
            Min = min(CoursesTaught), Max = max(CoursesTaught))

p1 <- ggplot(teaching_summary, aes(x = TeachingBinary, y = Percentage, fill = TeachingBinary)) +
  geom_col(show.legend = FALSE) +
  geom_text(aes(label = paste0(n, "\n(", Percentage, "%)")), vjust = -0.5, size = 4) +
  scale_y_continuous(limits = c(0, 100)) +
  scale_fill_manual(values = c("Yes" = aptc_teal, "No" = aptc_coral)) +
  labs(title = "Do Directors Teach?", x = NULL, y = "Percentage (%)") +
  theme_minimal(base_size = 12) +
  theme(plot.title = element_text(face = "bold", color = aptc_navy))

p2 <- dat %>%
  filter(TeachingBinary == "Yes", !is.na(CoursesTaught)) %>%
  ggplot(aes(x = CoursesTaught)) +
  geom_histogram(binwidth = 1, fill = aptc_teal, color = "white", alpha = 0.9) +
  labs(title = "Courses Taught per Year", subtitle = paste0("Among those who teach (n=", courses_summary$N, ")"),
       x = "Number of Courses", y = "Count") +
  theme_minimal(base_size = 12) +
  theme(plot.title = element_text(face = "bold", color = aptc_navy))

p1 + p2
```

# Clinic Characteristics

## Training Model and Clinic Age

```{r clinic-model}
model_summary <- dat %>% count(ClinicTrainingModel) %>% mutate(Percentage = round(100 * n / sum(n), 1)) %>% arrange(desc(n))

age_stats <- dat %>%
  filter(!is.na(ClinicAge), ClinicAge >= 0) %>%
  summarise(N = n(), Mean = mean(ClinicAge), SD = sd(ClinicAge), Median = median(ClinicAge),
            Min = min(ClinicAge), Max = max(ClinicAge))

p1 <- ggplot(model_summary, aes(x = reorder(ClinicTrainingModel, n), y = Percentage, fill = ClinicTrainingModel)) +
  geom_col(show.legend = FALSE) +
  geom_text(aes(label = paste0(n, "\n(", Percentage, "%)")), hjust = -0.2, size = 3) +
  coord_flip() + scale_y_continuous(limits = c(0, 100)) + scale_fill_manual(values = aptc_palette) +
  labs(title = "Training Model", x = NULL, y = "Percentage (%)") +
  theme_minimal(base_size = 11) + theme(plot.title = element_text(face = "bold", color = aptc_navy))

p2 <- dat %>%
  filter(!is.na(ClinicAge), ClinicAge >= 0) %>%
  ggplot(aes(x = ClinicAge)) +
  geom_histogram(binwidth = 10, fill = aptc_coral, color = "white", alpha = 0.9) +
  geom_vline(aes(xintercept = median(ClinicAge)), color = aptc_navy, linetype = "dashed", linewidth = 1) +
  labs(title = "Clinic Age (Years)", subtitle = paste0("Mean = ", round(age_stats$Mean, 1), " | Median = ", age_stats$Median),
       x = "Years", y = "Count") +
  theme_minimal(base_size = 11) + theme(plot.title = element_text(face = "bold", color = aptc_navy))

p1 + p2
```

## Trainees and Clients

```{r trainees-clients}
trainee_stats <- dat %>%
  filter(!is.na(ClinicTotalTrainees), ClinicTotalTrainees > 0) %>%
  summarise(N = n(), Mean = mean(ClinicTotalTrainees), SD = sd(ClinicTotalTrainees),
            Median = median(ClinicTotalTrainees), Min = min(ClinicTotalTrainees), Max = max(ClinicTotalTrainees))

client_stats <- dat %>%
  filter(!is.na(ClinicClientsCount), ClinicClientsCount > 0) %>%
  summarise(N = n(), Mean = mean(ClinicClientsCount), SD = sd(ClinicClientsCount),
            Median = median(ClinicClientsCount), Min = min(ClinicClientsCount), Max = max(ClinicClientsCount))

p1 <- dat %>%
  filter(!is.na(ClinicTotalTrainees), ClinicTotalTrainees > 0) %>%
  ggplot(aes(x = ClinicTotalTrainees)) +
  geom_histogram(binwidth = 5, fill = aptc_teal, color = "white", alpha = 0.9) +
  geom_vline(aes(xintercept = median(ClinicTotalTrainees)), color = aptc_coral, linetype = "dashed", linewidth = 1) +
  labs(title = "Trainees per Year", subtitle = paste0("Mean = ", round(trainee_stats$Mean, 1), " | Median = ", trainee_stats$Median),
       x = "Number of Trainees", y = "Count") +
  theme_minimal(base_size = 11) + theme(plot.title = element_text(face = "bold", color = aptc_navy))

p2 <- dat %>%
  filter(!is.na(ClinicClientsCount), ClinicClientsCount > 0) %>%
  ggplot(aes(x = ClinicClientsCount)) +
  geom_histogram(binwidth = 25, fill = aptc_coral, color = "white", alpha = 0.9) +
  geom_vline(aes(xintercept = median(ClinicClientsCount)), color = aptc_navy, linetype = "dashed", linewidth = 1) +
  labs(title = "Clients per Year", subtitle = paste0("Mean = ", round(client_stats$Mean, 1), " | Median = ", client_stats$Median),
       x = "Number of Clients", y = "Count") +
  theme_minimal(base_size = 11) + theme(plot.title = element_text(face = "bold", color = aptc_navy))

p1 + p2
```

## Clinic Services

```{r services}
therapy_binary <- dat %>% count(ClinicTherapyBinary) %>% mutate(Percentage = round(100 * n / sum(n), 1))
assmnt_binary <- dat %>% count(ClinicAssmntBinary) %>% mutate(Percentage = round(100 * n / sum(n), 1))

therapy_binary %>% kable(caption = "Clinics Offering Therapy Services") %>% kable_styling()
assmnt_binary %>% kable(caption = "Clinics Offering Assessment Services") %>% kable_styling()
```

## Client Populations Served

```{r client-populations}
pop_vars <- c("ClinicClientsPops_1" = "University Employees/Dependents", "ClinicClientsPops_2" = "University Students",
              "ClinicClientsPops_3" = "General Community", "ClinicClientsPops_4" = "Veterans/Military-connected",
              "ClinicClientsPops_6" = "Referred by Schools/Agencies", "ClinicClientsPops_5" = "Other")

pop_summary <- dat %>%
  select(starts_with("ClinicClientsPops_")) %>% select(-contains("TEXT")) %>%
  summarise(across(everything(), ~sum(!is.na(.) & . != "0" & . != "", na.rm = TRUE))) %>%
  pivot_longer(everything(), names_to = "Variable", values_to = "Count") %>%
  mutate(Population = pop_vars[Variable], Percentage = round(100 * Count / nrow(dat), 1)) %>%
  filter(!is.na(Population)) %>% arrange(desc(Count))

ggplot(pop_summary, aes(x = reorder(Population, Count), y = Percentage, fill = Population)) +
  geom_col(show.legend = FALSE) +
  geom_text(aes(label = paste0(Count, " (", Percentage, "%)")), hjust = -0.1, size = 3.5) +
  coord_flip() + scale_y_continuous(limits = c(0, 110)) + scale_fill_manual(values = aptc_palette) +
  labs(title = "Client Populations Served", subtitle = "Respondents could select multiple populations",
       x = NULL, y = "Percentage (%)") +
  theme_minimal(base_size = 13) +
  theme(plot.title = element_text(face = "bold", color = aptc_navy), panel.grid.minor = element_blank())
```

## Therapy Services Breakdown

```{r therapy-services}
therapy_vars <- c("ClinicTherapySvcs_1" = "Child Therapy", "ClinicTherapySvcs_2" = "Adolescent Therapy",
                  "ClinicTherapySvcs_3" = "Adult Therapy", "ClinicTherapySvcs_4" = "Older Adult Therapy",
                  "ClinicTherapySvcs_5" = "Couples Therapy", "ClinicTherapySvcs_6" = "Parent Training",
                  "ClinicTherapySvcs_7" = "Conjoint Family Therapy", "ClinicTherapySvcs_8" = "Group Therapy",
                  "ClinicTherapySvcs_9" = "Other")

therapy_summary <- dat %>%
  filter(ClinicTherapyBinary == "Yes") %>%
  select(starts_with("ClinicTherapySvcs_")) %>% select(-contains("TEXT")) %>%
  summarise(across(everything(), ~sum(!is.na(.) & . != "0" & . != "", na.rm = TRUE))) %>%
  pivot_longer(everything(), names_to = "Variable", values_to = "Count") %>%
  mutate(Service = therapy_vars[Variable],
         Percentage = round(100 * Count / sum(dat$ClinicTherapyBinary == "Yes", na.rm = TRUE), 1)) %>%
  filter(!is.na(Service)) %>% arrange(desc(Count))

ggplot(therapy_summary, aes(x = reorder(Service, Count), y = Percentage, fill = Service)) +
  geom_col(show.legend = FALSE) +
  geom_text(aes(label = paste0(Percentage, "%")), hjust = -0.1, size = 3.5) +
  coord_flip() + scale_y_continuous(limits = c(0, 110)) + scale_fill_manual(values = aptc_palette) +
  labs(title = "Therapy Services Offered", subtitle = "Among clinics providing therapy", x = NULL, y = "Percentage (%)") +
  theme_minimal(base_size = 13) +
  theme(plot.title = element_text(face = "bold", color = aptc_navy), panel.grid.minor = element_blank())
```

## Assessment Services Breakdown

```{r assessment-services}
assmnt_vars <- c("ClinicAssmntSvcs_1" = "Early Childhood (0-5)", "ClinicAssmntSvcs_2" = "Child/Adolescent Psychoeducational",
                 "ClinicAssmntSvcs_3" = "Child/Adolescent Neuropsychological", "ClinicAssmntSvcs_4" = "Adult Psychoeducational",
                 "ClinicAssmntSvcs_5" = "Adult Neuropsychological", "ClinicAssmntSvcs_6" = "Older Adult Neuropsychological",
                 "ClinicAssmntSvcs_7" = "Personality Testing", "ClinicAssmntSvcs_8" = "Projective Testing",
                 "ClinicAssmntSvcs_9" = "Forensic", "ClinicAssmntSvcs_10" = "Functional Behavioral Assessment",
                 "ClinicAssmntSvcs_11" = "School District Assessment", "ClinicAssmntSvcs_12" = "ADHD Testing",
                 "ClinicAssmntSvcs_13" = "Specific Learning Disorder", "ClinicAssmntSvcs_14" = "Autism Spectrum",
                 "ClinicAssmntSvcs_15" = "Memory Evaluations", "ClinicAssmntSvcs_16" = "Psychosocial Evaluations")

assmnt_summary <- dat %>%
  filter(ClinicAssmntBinary == "Yes") %>%
  select(starts_with("ClinicAssmntSvcs_")) %>% select(-contains("TEXT")) %>%
  summarise(across(everything(), ~sum(!is.na(.) & . != "0" & . != "", na.rm = TRUE))) %>%
  pivot_longer(everything(), names_to = "Variable", values_to = "Count") %>%
  mutate(Service = assmnt_vars[Variable],
         Percentage = round(100 * Count / sum(dat$ClinicAssmntBinary == "Yes", na.rm = TRUE), 1)) %>%
  filter(!is.na(Service)) %>% arrange(desc(Count))

ggplot(assmnt_summary, aes(x = reorder(Service, Count), y = Percentage, fill = Service)) +
  geom_col(show.legend = FALSE) +
  geom_text(aes(label = paste0(Percentage, "%")), hjust = -0.1, size = 2.5) +
  coord_flip() + scale_y_continuous(limits = c(0, 110)) + scale_fill_manual(values = rep(aptc_palette, 2)) +
  labs(title = "Assessment Services Offered", subtitle = "Among clinics providing assessment", x = NULL, y = "Percentage (%)") +
  theme_minimal(base_size = 11) +
  theme(plot.title = element_text(face = "bold", color = aptc_navy), panel.grid.minor = element_blank())
```

# Financial Information

## Sliding Scale

```{r sliding-scale}
sliding_scale <- dat %>% count(ClinicSlidingScale) %>% mutate(Percentage = round(100 * n / sum(n), 1))

ggplot(sliding_scale, aes(x = ClinicSlidingScale, y = Percentage, fill = ClinicSlidingScale)) +
  geom_col(show.legend = FALSE) +
  geom_text(aes(label = paste0(n, " (", Percentage, "%)")), vjust = -0.5, size = 5) +
  scale_y_continuous(limits = c(0, 100), breaks = seq(0, 100, 20)) +
  scale_fill_manual(values = c("Yes" = aptc_teal, "No" = aptc_coral)) +
  labs(title = "Do Clinics Offer a Sliding Scale?", x = NULL, y = "Percentage (%)") +
  theme_minimal(base_size = 13) +
  theme(plot.title = element_text(face = "bold", color = aptc_navy))
```

## Clinic Revenue

```{r revenue}
revenue_stats <- dat %>%
  filter(!is.na(ClinicRevenue), ClinicRevenue > 0) %>%
  summarise(N = n(), Mean = mean(ClinicRevenue), SD = sd(ClinicRevenue), Median = median(ClinicRevenue),
            Q1 = quantile(ClinicRevenue, 0.25), Q3 = quantile(ClinicRevenue, 0.75),
            Min = min(ClinicRevenue), Max = max(ClinicRevenue))

dat %>%
  filter(!is.na(ClinicRevenue), ClinicRevenue > 0, ClinicRevenue < 500000) %>%
  ggplot(aes(x = ClinicRevenue)) +
  geom_histogram(binwidth = 25000, fill = aptc_teal, color = "white", alpha = 0.9) +
  geom_vline(aes(xintercept = median(ClinicRevenue, na.rm = TRUE)), color = aptc_coral, linetype = "dashed", linewidth = 1) +
  scale_x_continuous(labels = dollar_format()) +
  labs(title = "Annual Clinic Revenue Distribution",
       subtitle = paste0("Median = ", dollar(revenue_stats$Median), " | Mean = ", dollar(revenue_stats$Mean)),
       x = "Annual Revenue", y = "Count") +
  theme_minimal(base_size = 13) +
  theme(plot.title = element_text(face = "bold", color = aptc_navy))
```

## Fee Structures

```{r fee-structures}
therapy_fee_vars <- c("ClinicTherapyFees_1", "ClinicTherapyFees_2", "ClinicTherapyFees_3")

therapy_fees <- dat %>%
  select(all_of(therapy_fee_vars)) %>%
  mutate(across(everything(), as.numeric)) %>%
  pivot_longer(everything(), names_to = "Variable", values_to = "Fee") %>%
  filter(!is.na(Fee), Fee >= 0) %>%
  mutate(Type = case_when(Variable == "ClinicTherapyFees_1" ~ "Minimum",
                          Variable == "ClinicTherapyFees_2" ~ "Maximum",
                          Variable == "ClinicTherapyFees_3" ~ "Typical")) %>%
  group_by(Type) %>%
  summarise(N = n(), Mean = mean(Fee), Median = median(Fee), Min = min(Fee), Max = max(Fee), .groups = "drop")

assmnt_fee_vars <- c("ClinicAssmntFees_1", "ClinicAssmntFees_2", "ClinicAssmntFees_3")

assmnt_fees <- dat %>%
  select(all_of(assmnt_fee_vars)) %>%
  mutate(across(everything(), as.numeric)) %>%
  pivot_longer(everything(), names_to = "Variable", values_to = "Fee") %>%
  filter(!is.na(Fee), Fee >= 0) %>%
  mutate(Type = case_when(Variable == "ClinicAssmntFees_1" ~ "Minimum",
                          Variable == "ClinicAssmntFees_2" ~ "Maximum",
                          Variable == "ClinicAssmntFees_3" ~ "Typical")) %>%
  group_by(Type) %>%
  summarise(N = n(), Mean = mean(Fee), Median = median(Fee), Min = min(Fee), Max = max(Fee), .groups = "drop")

fee_summary <- bind_rows(therapy_fees %>% mutate(Service = "Therapy"),
                         assmnt_fees %>% mutate(Service = "Assessment")) %>%
  select(Service, Type, N, Mean, Median, Min, Max) %>%
  arrange(Service, factor(Type, levels = c("Minimum", "Typical", "Maximum")))

fee_summary %>%
  mutate(across(c(Mean, Median, Min, Max), ~dollar(round(.)))) %>%
  kable(caption = "Standard Fee Structures") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```

## Insurance Billing

```{r insurance-billing}
billing_summary <- dat %>% count(ClinicBillBinary) %>% mutate(Percentage = round(100 * n / sum(n), 1))

billing_summary %>%
  kable(caption = "Does Your Clinic Bill Insurance?") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```

## Revenue by Client Count

```{r revenue-clients}
dat_revenue <- dat %>%
  filter(!is.na(ClinicRevenue), !is.na(ClinicClientsCount), ClinicRevenue > 0, ClinicClientsCount > 0, ClinicRevenue < 1000000) %>%
  mutate(ClinicSize = case_when(ClinicClientsCount < 93 ~ "Small (<93)",
                                 ClinicClientsCount >= 93 & ClinicClientsCount <= 130 ~ "Medium (93-130)",
                                 ClinicClientsCount > 130 ~ "Large (>130)"),
         ClinicSize = factor(ClinicSize, levels = c("Small (<93)", "Medium (93-130)", "Large (>130)")))

cor_result <- cor.test(dat_revenue$ClinicClientsCount, dat_revenue$ClinicRevenue)

ggplot(dat_revenue, aes(x = ClinicClientsCount, y = ClinicRevenue, color = ClinicSize)) +
  geom_point(size = 3, alpha = 0.7) +
  geom_smooth(method = "lm", se = TRUE, color = aptc_navy, linetype = "dashed") +
  scale_y_continuous(labels = dollar_format()) +
  scale_color_manual(values = c("Small (<93)" = aptc_coral, "Medium (93-130)" = aptc_teal, "Large (>130)" = aptc_navy)) +
  labs(title = "Clinic Revenue by Client Number", subtitle = paste0("Correlation: r = ", round(cor_result$estimate, 2)),
       x = "Number of Clients per Year", y = "Annual Clinic Revenue", color = "Clinic Size") +
  theme_minimal(base_size = 13) +
  theme(plot.title = element_text(face = "bold", color = aptc_navy), legend.position = "top")
```

# Staff and Operations

## Clinic Space

```{r clinic-space}
sqft_stats <- dat %>%
  filter(!is.na(ClinSqFt), ClinSqFt > 0) %>%
  summarise(N = n(), Mean = mean(ClinSqFt), SD = sd(ClinSqFt), Median = median(ClinSqFt),
            Min = min(ClinSqFt), Max = max(ClinSqFt))

sqft_stats %>%
  mutate(across(where(is.numeric) & !matches("^N$"), ~format(round(.), big.mark = ","))) %>%
  kable(caption = "Clinic Square Footage") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

dat %>%
  filter(!is.na(ClinSqFt), ClinSqFt > 0, ClinSqFt < 20000) %>%
  ggplot(aes(x = ClinSqFt)) +
  geom_histogram(binwidth = 500, fill = aptc_teal, color = "white", alpha = 0.9) +
  geom_vline(aes(xintercept = median(ClinSqFt)), color = aptc_coral, linetype = "dashed", linewidth = 1) +
  scale_x_continuous(labels = comma_format()) +
  labs(title = "Clinic Space Distribution",
       subtitle = paste0("Median = ", format(round(sqft_stats$Median), big.mark = ","), " sq ft"),
       x = "Square Feet", y = "Count") +
  theme_minimal(base_size = 13) +
  theme(plot.title = element_text(face = "bold", color = aptc_navy))
```

## Number of Rooms

```{r rooms}
room_stats <- dat %>%
  filter(!is.na(NumRooms), NumRooms > 0) %>%
  summarise(N = n(), Mean = mean(NumRooms), SD = sd(NumRooms), Median = median(NumRooms),
            Min = min(NumRooms), Max = max(NumRooms))

dat %>%
  filter(!is.na(NumRooms), NumRooms > 0) %>%
  ggplot(aes(x = NumRooms)) +
  geom_histogram(binwidth = 2, fill = aptc_teal, color = "white", alpha = 0.9) +
  geom_vline(aes(xintercept = median(NumRooms)), color = aptc_coral, linetype = "dashed", linewidth = 1) +
  labs(title = "Number of Clinic Rooms",
       subtitle = paste0("Mean = ", round(room_stats$Mean, 1), " | Median = ", room_stats$Median),
       x = "Number of Rooms", y = "Count") +
  theme_minimal(base_size = 13) +
  theme(plot.title = element_text(face = "bold", color = aptc_navy))
```

## Supervisors and Caseloads

```{r supervisors}
max_trainee_summary <- dat %>%
  filter(!is.na(MaxTraineeCount), MaxTraineeCount > 0) %>%
  summarise(N = n(), Mean = mean(MaxTraineeCount), SD = sd(MaxTraineeCount), Median = median(MaxTraineeCount),
            Min = min(MaxTraineeCount), Max = max(MaxTraineeCount))

dat %>%
  filter(!is.na(MaxTraineeCount), MaxTraineeCount > 0) %>%
  ggplot(aes(x = MaxTraineeCount)) +
  geom_histogram(binwidth = 2, fill = aptc_coral, color = "white", alpha = 0.9) +
  geom_vline(aes(xintercept = median(MaxTraineeCount)), color = aptc_navy, linetype = "dashed", linewidth = 1) +
  labs(title = "Maximum Trainees per Supervisor",
       subtitle = paste0("Mean = ", round(max_trainee_summary$Mean, 1), " | Median = ", max_trainee_summary$Median),
       x = "Max Trainees", y = "Count") +
  theme_minimal(base_size = 13) +
  theme(plot.title = element_text(face = "bold", color = aptc_navy))
```

```{r max-caseload-details}
caseload_vars <- tibble(Variable = c("MaxTraineesTherapy", "MaxTraineesAssmnt", "MaxTxCasesAllow", "MaxAxCasesAllow"),
                        Metric = c("Max Therapy Trainees", "Max Assessment Trainees",
                                   "Max Therapy Cases Allowed", "Max Assessment Cases Allowed"))

caseload_summary <- dat %>%
  select(all_of(caseload_vars$Variable)) %>%
  pivot_longer(everything(), names_to = "Variable", values_to = "Value") %>%
  filter(!is.na(Value), Value > 0) %>%
  left_join(caseload_vars, by = "Variable") %>%
  group_by(Metric) %>%
  summarise(N = n(), Mean = mean(Value), SD = sd(Value), Median = median(Value),
            Min = min(Value), Max = max(Value), .groups = "drop")

caseload_summary %>%
  mutate(across(where(is.numeric) & !matches("^N$"), ~round(., 1))) %>%
  kable(caption = "Student Caseload & Supervisor Team Size") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```

## Staff Details

```{r staff-details}
staff_vars <- tibble(Variable = c("FTESupportStaff", "ClinicSupportStaff", "FTEGradStaff", "GradStaff", "UgradStaff", "PostdocCount"),
                     Staff_Type = c("Support Staff (FTE)", "Support Staff (Count)", "Graduate Staff (FTE)",
                                    "Graduate Staff (Count)", "Undergraduate Staff", "Postdocs"))

staff_summary <- dat %>%
  select(any_of(staff_vars$Variable)) %>%
  mutate(across(everything(), as.numeric)) %>%
  pivot_longer(everything(), names_to = "Variable", values_to = "Value") %>%
  filter(!is.na(Value), Value >= 0) %>%
  left_join(staff_vars, by = "Variable") %>%
  group_by(Staff_Type) %>%
  summarise(N = n(), Mean = mean(Value), SD = sd(Value), Median = median(Value),
            Min = min(Value), Max = max(Value), .groups = "drop") %>%
  filter(!is.na(Staff_Type))

staff_summary %>%
  mutate(across(where(is.numeric) & !matches("^N$"), ~round(., 1))) %>%
  kable(caption = "Clinic Staff Summary") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

staff_presence <- dat %>%
  summarise(`Has Support Staff` = mean(as.numeric(ClinicSupportStaff) > 0, na.rm = TRUE) * 100,
            `Has Grad Staff` = mean(as.numeric(GradStaff) > 0, na.rm = TRUE) * 100,
            `Has Undergrad Staff` = mean(as.numeric(UgradStaff) > 0, na.rm = TRUE) * 100,
            `Has Postdocs` = mean(as.numeric(PostdocCount) > 0, na.rm = TRUE) * 100) %>%
  pivot_longer(everything(), names_to = "Staff Type", values_to = "Percentage")

ggplot(staff_presence, aes(x = reorder(`Staff Type`, Percentage), y = Percentage, fill = `Staff Type`)) +
  geom_col(show.legend = FALSE) +
  geom_text(aes(label = paste0(round(Percentage, 0), "%")), hjust = -0.1, size = 4) +
  coord_flip() + scale_y_continuous(limits = c(0, 100)) + scale_fill_manual(values = aptc_palette) +
  labs(title = "Percentage of Clinics with Various Staff Types", x = NULL, y = "Percentage (%)") +
  theme_minimal(base_size = 13) +
  theme(plot.title = element_text(face = "bold", color = aptc_navy))
```

## Clinic Hours

```{r clinic-hours}
clinic_hours_stats <- dat %>%
  mutate(ClinicHours = as.numeric(ClinicHours)) %>%
  filter(!is.na(ClinicHours), ClinicHours > 0) %>%
  summarise(N = n(), Mean = mean(ClinicHours), SD = sd(ClinicHours), Median = median(ClinicHours),
            Min = min(ClinicHours), Max = max(ClinicHours))

clinic_hours_stats %>%
  mutate(across(where(is.numeric) & !matches("^N$"), ~round(., 1))) %>%
  kable(caption = "Clinic Operating Hours per Week") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

dat %>%
  mutate(ClinicHours = as.numeric(ClinicHours)) %>%
  filter(!is.na(ClinicHours), ClinicHours > 0) %>%
  ggplot(aes(x = ClinicHours)) +
  geom_histogram(binwidth = 5, fill = aptc_teal, color = "white", alpha = 0.9) +
  geom_vline(aes(xintercept = median(ClinicHours)), color = aptc_coral, linetype = "dashed", linewidth = 1) +
  labs(title = "Clinic Operating Hours per Week",
       subtitle = paste0("Median = ", clinic_hours_stats$Median, " hours | Mean = ", round(clinic_hours_stats$Mean, 1), " hours"),
       x = "Hours per Week", y = "Count") +
  theme_minimal(base_size = 13) +
  theme(plot.title = element_text(face = "bold", color = aptc_navy))
```

# Technology

## EMR Usage

```{r emr}
emr_summary <- dat %>% count(EMRbinary) %>% mutate(Percentage = round(100 * n / sum(n), 1))

ggplot(emr_summary, aes(x = EMRbinary, y = Percentage, fill = EMRbinary)) +
  geom_col(show.legend = FALSE) +
  geom_text(aes(label = paste0(n, " (", Percentage, "%)")), vjust = -0.5, size = 5) +
  scale_y_continuous(limits = c(0, 100), breaks = seq(0, 100, 20)) +
  scale_fill_manual(values = c("Yes" = aptc_teal, "No" = aptc_coral)) +
  labs(title = "Electronic Medical Record (EMR) Usage", x = "Uses EMR?", y = "Percentage (%)") +
  theme_minimal(base_size = 13) +
  theme(plot.title = element_text(face = "bold", color = aptc_navy))
```

## Telehealth

```{r telehealth}
telehealth_summary <- dat %>% count(Telehealth) %>% mutate(Percentage = round(100 * n / sum(n), 1))

ggplot(telehealth_summary, aes(x = Telehealth, y = Percentage, fill = Telehealth)) +
  geom_col(show.legend = FALSE) +
  geom_text(aes(label = paste0(n, " (", Percentage, "%)")), vjust = -0.5, size = 5) +
  scale_y_continuous(limits = c(0, 100), breaks = seq(0, 100, 20)) +
  scale_fill_manual(values = aptc_palette) +
  labs(title = "Telehealth Service Provision", x = "Offers Telehealth?", y = "Percentage (%)") +
  theme_minimal(base_size = 13) +
  theme(plot.title = element_text(face = "bold", color = aptc_navy))
```

```{r telehealth-usage}
telehealth_usage <- dat %>%
  select(PercTxTelehealth_1, PercAxTelehealth_1, PercClinSupTele_1) %>%
  mutate(across(everything(), as.numeric)) %>%
  pivot_longer(everything(), names_to = "Variable", values_to = "Percent_InPerson") %>%
  filter(!is.na(Percent_InPerson)) %>%
  mutate(Service = case_when(Variable == "PercTxTelehealth_1" ~ "Therapy",
                             Variable == "PercAxTelehealth_1" ~ "Assessment",
                             Variable == "PercClinSupTele_1" ~ "Supervision"),
         Percent_Telehealth = 100 - Percent_InPerson) %>%
  group_by(Service) %>%
  summarise(N = n(), Mean_InPerson = mean(Percent_InPerson), Mean_Telehealth = mean(Percent_Telehealth),
            Median_InPerson = median(Percent_InPerson), Median_Telehealth = median(Percent_Telehealth), .groups = "drop")

telehealth_usage %>%
  mutate(across(where(is.numeric) & !matches("^N$"), ~round(., 1))) %>%
  kable(caption = "Telehealth vs In-Person Service Delivery (%)") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

telehealth_plot_data <- telehealth_usage %>%
  select(Service, Mean_InPerson, Mean_Telehealth) %>%
  pivot_longer(cols = c(Mean_InPerson, Mean_Telehealth), names_to = "Modality", values_to = "Percentage") %>%
  mutate(Modality = ifelse(Modality == "Mean_InPerson", "In-Person", "Telehealth"))

ggplot(telehealth_plot_data, aes(x = Service, y = Percentage, fill = Modality)) +
  geom_col(position = "dodge", alpha = 0.9) +
  geom_text(aes(label = paste0(round(Percentage), "%")), position = position_dodge(width = 0.9), vjust = -0.5, size = 3.5) +
  scale_fill_manual(values = c("In-Person" = aptc_teal, "Telehealth" = aptc_coral)) +
  scale_y_continuous(limits = c(0, 100)) +
  labs(title = "Service Delivery by Modality", subtitle = "Mean percentage of services delivered in-person vs telehealth",
       x = NULL, y = "Percentage (%)", fill = "Modality") +
  theme_minimal(base_size = 13) +
  theme(plot.title = element_text(face = "bold", color = aptc_navy), legend.position = "top")
```

## Artificial Intelligence

```{r ai}
ai_clindir <- dat %>% count(AIUseClinDir) %>% mutate(Percentage = round(100 * n / sum(n), 1))
ai_students <- dat %>% count(AIUseStudentsAllowed) %>% mutate(Percentage = round(100 * n / sum(n), 1))

p1 <- ggplot(ai_clindir, aes(x = AIUseClinDir, y = Percentage, fill = AIUseClinDir)) +
  geom_col(show.legend = FALSE) +
  geom_text(aes(label = paste0(Percentage, "%")), vjust = -0.5, size = 4) +
  scale_y_continuous(limits = c(0, 100)) + scale_fill_manual(values = aptc_palette) +
  labs(title = "AI Use by Clinic Directors", x = NULL, y = "Percentage (%)") +
  theme_minimal(base_size = 11) + theme(plot.title = element_text(face = "bold", color = aptc_navy))

p2 <- ggplot(ai_students, aes(x = AIUseStudentsAllowed, y = Percentage, fill = AIUseStudentsAllowed)) +
  geom_col(show.legend = FALSE) +
  geom_text(aes(label = paste0(Percentage, "%")), vjust = -0.5, size = 4) +
  scale_y_continuous(limits = c(0, 100)) + scale_fill_manual(values = aptc_palette) +
  labs(title = "AI Use Allowed for Students", x = NULL, y = "Percentage (%)") +
  theme_minimal(base_size = 11) +
  theme(plot.title = element_text(face = "bold", color = aptc_navy), axis.text.x = element_text(angle = 20, hjust = 1))

p1 + p2
```

```{r ai-policy}
ai_policy <- dat %>% count(AIPolicy) %>% mutate(Percentage = round(100 * n / sum(n), 1))

ai_policy %>%
  kable(caption = "Does Your Clinic Have an AI Policy?") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```

## Routine Outcome Monitoring (ROM)

```{r rom}
rom_vars <- c("ROMsystem_1" = "OQ-45", "ROMsystem_2" = "PHQ-9/GAD-7", "ROMsystem_3" = "PCOMS/ORS",
              "ROMsystem_4" = "Standardized Assessment Battery", "ROMsystem_5" = "Custom/Clinic-developed",
              "ROMsystem_6" = "Other")

rom_summary <- dat %>%
  select(starts_with("ROMsystem_")) %>% select(-contains("TEXT")) %>%
  summarise(across(everything(), ~sum(!is.na(.) & . != "0" & . != "", na.rm = TRUE))) %>%
  pivot_longer(everything(), names_to = "Variable", values_to = "Count") %>%
  mutate(System = rom_vars[Variable], Percentage = round(100 * Count / nrow(dat), 1)) %>%
  filter(!is.na(System), Count > 0) %>% arrange(desc(Count))

if(nrow(rom_summary) > 0) {
  ggplot(rom_summary, aes(x = reorder(System, Count), y = Percentage, fill = System)) +
    geom_col(show.legend = FALSE) +
    geom_text(aes(label = paste0(Count, " (", Percentage, "%)")), hjust = -0.1, size = 3.5) +
    coord_flip() + scale_y_continuous(limits = c(0, max(rom_summary$Percentage) + 15)) +
    scale_fill_manual(values = aptc_palette) +
    labs(title = "Routine Outcome Monitoring Systems Used", subtitle = "Respondents could select multiple systems",
         x = NULL, y = "Percentage (%)") +
    theme_minimal(base_size = 13) +
    theme(plot.title = element_text(face = "bold", color = aptc_navy), panel.grid.minor = element_blank())
  
  rom_summary %>%
    select(System, Count, Percentage) %>%
    kable(caption = "ROM Systems Used (Select All That Apply)") %>%
    kable_styling(bootstrap_options = c("striped", "hover"))
}
```

# Social Justice & DEI Efforts

```{r dei-activities}
dei_vars <- c("ClinicSJActivities_1" = "Resources on antiracism - students",
              "ClinicSJActivities_2" = "Resources on antiracism - supervisors",
              "ClinicSJActivities_3" = "New/specialized services for BIPOC clients",
              "ClinicSJActivities_4" = "Outreach to marginalized communities",
              "ClinicSJActivities_5" = "Added DEI didactics/training",
              "ClinicSJActivities_6" = "Significant changes to syllabi",
              "ClinicSJActivities_7" = "New supervisors/instructors for DEI",
              "ClinicSJActivities_8" = "CCTC toolkit on social responsiveness",
              "ClinicSJActivities_9" = "Other")

dei_summary <- dat %>%
  select(starts_with("ClinicSJActivities_")) %>% select(-contains("TEXT")) %>%
  summarise(across(everything(), ~sum(!is.na(.) & . != "0" & . != "", na.rm = TRUE))) %>%
  pivot_longer(everything(), names_to = "Variable", values_to = "Count") %>%
  mutate(Activity = dei_vars[Variable], Percentage = round(100 * Count / nrow(dat), 1)) %>%
  filter(!is.na(Activity)) %>% arrange(desc(Count))

ggplot(dei_summary, aes(x = reorder(Activity, Count), y = Percentage, fill = Activity)) +
  geom_col(show.legend = FALSE) +
  geom_text(aes(label = paste0(Percentage, "%")), hjust = -0.1, size = 3) +
  coord_flip() + scale_y_continuous(limits = c(0, max(dei_summary$Percentage) + 15)) +
  scale_fill_manual(values = rep(aptc_palette, 2)) +
  labs(title = "Social Justice & DEI Activities", subtitle = "Respondents could select multiple activities",
       x = NULL, y = "Percentage (%)") +
  theme_minimal(base_size = 11) +
  theme(plot.title = element_text(face = "bold", color = aptc_navy), panel.grid.minor = element_blank())

dei_summary %>%
  select(Activity, Count, Percentage) %>%
  kable(caption = "Social Justice & DEI Activities (Select All That Apply)") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```

# Research Activities

```{r research}
research_summary <- dat %>% count(ResearchActive) %>% mutate(Percentage = round(100 * n / sum(n), 1))

ggplot(research_summary, aes(x = ResearchActive, y = Percentage, fill = ResearchActive)) +
  geom_col(show.legend = FALSE) +
  geom_text(aes(label = paste0(n, " (", Percentage, "%)")), vjust = -0.5, size = 4) +
  scale_y_continuous(limits = c(0, 100), breaks = seq(0, 100, 20)) +
  scale_fill_manual(values = aptc_palette) +
  labs(title = "Research Activity in Training Clinics", x = "Research Status", y = "Percentage (%)") +
  theme_minimal(base_size = 13) +
  theme(plot.title = element_text(face = "bold", color = aptc_navy), axis.text.x = element_text(angle = 15, hjust = 1))
```

# Burnout and Job Satisfaction

## Burnout Levels (Single Item)

```{r burnout-single}
burnout_stats <- dat %>%
  filter(!is.na(Burnout_1)) %>%
  summarise(N = n(), Mean = mean(Burnout_1), SD = sd(Burnout_1), Median = median(Burnout_1),
            Min = min(Burnout_1), Max = max(Burnout_1))

dat %>%
  filter(!is.na(Burnout_1)) %>%
  ggplot(aes(x = Burnout_1)) +
  geom_histogram(binwidth = 1, fill = aptc_coral, color = "white", alpha = 0.9) +
  geom_vline(aes(xintercept = mean(Burnout_1)), color = aptc_navy, linetype = "dashed", linewidth = 1) +
  scale_x_continuous(breaks = 0:6) +
  labs(title = "Burnout Levels Among Clinic Directors",
       subtitle = paste0("Mean = ", round(burnout_stats$Mean, 2), " (SD = ", round(burnout_stats$SD, 2), ") | Range: 0-6"),
       x = "Burnout Score (0 = No burnout, 6 = Severe burnout)", y = "Count") +
  theme_minimal(base_size = 13) +
  theme(plot.title = element_text(face = "bold", color = aptc_navy))
```

## Copenhagen Burnout Inventory (CBI) Scale

The CBI assesses multiple dimensions of work-related burnout. Items are rated on a scale where higher scores indicate greater burnout.

```{r burnout-cbi}
cbi_vars <- tibble(Variable = c("Burnout_1", "Burnout_2", "Burnout_3", "Burnout_4", "Burnout_5"),
                   Item = c("How often do you feel tired?", "How often are you physically exhausted?",
                            "Do you feel burned out because of your work?",
                            "Do you feel worn out at the end of the working day?",
                            "Do you find it hard to work with clients?"))

cbi_summary <- dat %>%
  select(all_of(cbi_vars$Variable)) %>%
  pivot_longer(everything(), names_to = "Variable", values_to = "Score") %>%
  filter(!is.na(Score)) %>%
  left_join(cbi_vars, by = "Variable") %>%
  group_by(Item) %>%
  summarise(N = n(), Mean = mean(Score), SD = sd(Score), Median = median(Score), .groups = "drop") %>%
  arrange(desc(Mean))

cbi_summary %>%
  mutate(across(where(is.numeric) & !matches("^N$"), ~round(., 2))) %>%
  kable(caption = "Copenhagen Burnout Inventory (CBI) Item Summary") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

dat <- dat %>%
  rowwise() %>%
  mutate(Burnout_Composite = mean(c(Burnout_1, Burnout_2, Burnout_3, Burnout_4, Burnout_5), na.rm = TRUE)) %>%
  ungroup()

burnout_composite_stats <- dat %>%
  filter(!is.na(Burnout_Composite)) %>%
  summarise(N = n(), Mean = mean(Burnout_Composite), SD = sd(Burnout_Composite),
            Median = median(Burnout_Composite), Min = min(Burnout_Composite), Max = max(Burnout_Composite))

dat %>%
  filter(!is.na(Burnout_Composite)) %>%
  ggplot(aes(x = Burnout_Composite)) +
  geom_histogram(binwidth = 0.5, fill = aptc_coral, color = "white", alpha = 0.9) +
  geom_vline(aes(xintercept = mean(Burnout_Composite)), color = aptc_navy, linetype = "dashed", linewidth = 1) +
  scale_x_continuous(breaks = 0:6) +
  labs(title = "CBI Composite Burnout Score Distribution",
       subtitle = paste0("Mean = ", round(burnout_composite_stats$Mean, 2), " (SD = ", round(burnout_composite_stats$SD, 2), ")"),
       x = "Composite Burnout Score (0-6)", y = "Count") +
  theme_minimal(base_size = 13) +
  theme(plot.title = element_text(face = "bold", color = aptc_navy))

cbi_plot_data <- dat %>%
  select(all_of(cbi_vars$Variable)) %>%
  pivot_longer(everything(), names_to = "Variable", values_to = "Score") %>%
  filter(!is.na(Score)) %>%
  left_join(cbi_vars, by = "Variable") %>%
  mutate(Item = str_wrap(Item, width = 30))

ggplot(cbi_plot_data, aes(x = reorder(Item, Score, FUN = mean), y = Score, fill = Item)) +
  geom_boxplot(alpha = 0.8, show.legend = FALSE) +
  coord_flip() + scale_fill_manual(values = aptc_palette) +
  labs(title = "Burnout by CBI Item", subtitle = "Higher scores indicate greater burnout (0-6 scale)",
       x = NULL, y = "Burnout Score") +
  theme_minimal(base_size = 12) +
  theme(plot.title = element_text(face = "bold", color = aptc_navy))
```

## Burnout by Position Characteristics

```{r burnout-by-position}
burnout_by_tt <- dat %>%
  filter(!is.na(Burnout_Composite), !is.na(PositionType)) %>%
  mutate(TenureStatus = case_when(is_tt(PositionType) ~ "TT/Tenured",
                                   is_ntt(PositionType) ~ "Non-Tenure-Track",
                                   TRUE ~ "Other")) %>%
  group_by(TenureStatus) %>%
  summarise(N = n(), Mean = mean(Burnout_Composite), SD = sd(Burnout_Composite),
            Median = median(Burnout_Composite), .groups = "drop")

burnout_by_tt %>%
  mutate(across(where(is.numeric) & !matches("^N$"), ~round(., 2))) %>%
  kable(caption = "Composite Burnout by Tenure Track Status") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

burnout_by_rank <- dat_simple %>%
  filter(!is.na(Burnout_1), !is.na(RankGrp)) %>%
  group_by(RankGrp) %>%
  summarise(N = n(), Mean = mean(Burnout_1, na.rm = TRUE), SD = sd(Burnout_1, na.rm = TRUE), .groups = "drop") %>%
  filter(N >= 3)

if(nrow(burnout_by_rank) > 0) {
  ggplot(burnout_by_rank, aes(x = reorder(RankGrp, Mean), y = Mean, fill = RankGrp)) +
    geom_col(show.legend = FALSE) +
    geom_errorbar(aes(ymin = pmax(0, Mean - SD), ymax = Mean + SD), width = 0.2, color = aptc_navy) +
    geom_text(aes(label = paste0("n=", N)), vjust = -0.5, size = 3) +
    coord_flip() + scale_fill_manual(values = aptc_palette) +
    labs(title = "Burnout by Academic Rank", subtitle = "Error bars = ±1 SD", x = NULL, y = "Mean Burnout Score (0-6)") +
    theme_minimal(base_size = 13) +
    theme(plot.title = element_text(face = "bold", color = aptc_navy))
}
```

# Session Information

```{r session}
sessionInfo()
```
